---
title: "Analysis_final"
author: "Lisa Mijares"
date: "2025-07-22"
output: html_document
---

# Introduction 

This objective of this markdown is to conduct a meta-analysis on the difference between the toxicity of active ingredients and formulations in pesticides. It necessitates to have extracted effect sizes beforehand, and to have a csv file containing the relevant columns. The files used in the study are available. 

As this markdown is used for the results and figures of my dissertation, its' affected with  major decisions: include phylogenetic lacking data, only consider three class of pesticides, and using majoritarily the imputation results. For results not affected by those decisions, consult the old markdown. 

# Code 
 
## Packages set up 

```{r, message=FALSE, warning=FALSE}
# Importing packages
library(tidyverse)
library(metafor)
library(metagear)
library(drc)
library(metaAidR)
library(ape)
library(rotl)
library(corrplot)
library(MuMIn)
library(clubSandwich)
library(emmeans)
library(orchaRd)
library(fitdistrplus)
library(kableExtra)
library(cowplot)
library(webshot2)
library(patchwork)
library(ggbeeswarm)
```

```{r}
# This chunk allows to install the packages that are not directly available on CRAN, it only needs to be run once

#library(remotes)
#remotes::install_github("daniel1noble/metaAidR")
#library(devtools)
#devtools::install_github("daniel1noble/orchaRd", force = TRUE)

```

```{r}
# This is from the Nagawaka et al tutorial, the file needs to be at the same place than the current markdown 
source("./func.R")
```


## Getting the data 

```{r}
set.seed(42)
```

```{r, message=FALSE, warning=FALSE}
# Getting the data 
guy_data <- read_csv("Input/data_extraction_Guy_formatted.csv") %>%
  mutate(SOURCE= "Guy")
lisa_data <- read_csv("Input/data_extraction_Lisa_formatted.csv") %>%
  mutate(SOURCE = "Lisa") %>%
  mutate(STUDY_ID = as.character(STUDY_ID)) %>% # because Guy has letters in his study ids  
  mutate(PH = as.character(PH)) %>% # because Guy has comments in the PH column
# Changing the data id in my dataset so there's no duplicates
  mutate(DATA_ID = DATA_ID + nrow(guy_data))

#Joining the data

all_data <- bind_rows(guy_data, lisa_data)
```


## Preparing the data

### Cleaning and separating into smaller datasets 

```{r, message=FALSE, warning=FALSE}

# Cleaning

all_data_formatted <- all_data %>%
  # Remove the > signs from the values 
  mutate(AI_50 = str_remove(AI_50, ">") %>% as.numeric()) %>%
  mutate(FORM_50 = str_remove(FORM_50, ">") %>% as.numeric()) %>%
  mutate(FORMULATION_TYPE = FORMULATION_TYPE %>%
             str_remove("s$") %>%   # Remove trailing 's'
             str_to_lower()) %>%
  mutate(PESTICIDE_CLASS = str_to_lower(PESTICIDE_CLASS)) %>%
  mutate(EXPOSURE_ROUTE = str_to_lower(EXPOSURE_ROUTE)) %>%
  mutate(AI_NAME = str_to_lower(AI_NAME))

# Separating between rows with error and missing error 
data_no_missing <- all_data_formatted %>%
  drop_na(FORM_ERROR_TYPE) %>%
  drop_na(AI_ERROR_TYPE)

data_missing_error <- all_data_formatted %>%
  filter(is.na(AI_ERROR_TYPE) | is.na(FORM_ERROR_TYPE))

# Could also have use the variable SE_SIMULATION_REQUIRED 

# Excluding some rows

data_cleaned <- data_no_missing %>%
  # Excluding of not same error type 
  filter(AI_ERROR_TYPE == FORM_ERROR_TYPE) %>%
  # Excluding if both arms are <0
  filter((AI_ERROR_HIGHER > 0 | AI_ERROR_LOWER > 0) &
         (FORM_ERROR_LOWER > 0 | FORM_ERROR_HIGHER > 0))

# Keeping traces of excluded rows 
excluded <- data_no_missing %>%
  filter(AI_ERROR_TYPE != FORM_ERROR_TYPE) %>%
  mutate(REASON_EXCLUSION = "Not_same_error_type") %>% 
  bind_rows(data_no_missing %>%  
              filter((AI_ERROR_LOWER <= 0 & AI_ERROR_HIGHER <= 0) |
                       (FORM_ERROR_LOWER <= 0 & FORM_ERROR_HIGHER <= 0)) %>%
              mutate(REASON_EXCLUSION = "Both_error_negative_or_null"))
    
# Separating according to the type of error 

# Creating a df with rows where the error is a CI
data_CI <- data_cleaned %>%
  filter(AI_ERROR_TYPE == "CI_95")

# Creating a df with rows where the error is a SE
data_SE <- data_cleaned %>%
  filter(AI_ERROR_TYPE == "SE")

# Creating a df with rows where the error is a SD
data_SD <- data_cleaned %>%
  filter(AI_ERROR_TYPE == "SD")

```

```{r}
# Some checks to be sure that rows have not been lost 
nrow(data_no_missing) + nrow(data_missing_error) == nrow(all_data_formatted)
nrow(excluded) + nrow(data_cleaned) == nrow(data_no_missing)
nrow(data_CI) + nrow(data_SD) + nrow(data_SE) == nrow(data_cleaned)
```
### Converting all errors in SE (standard errors)

A consequent number of rows have a CI or SD as their measurement of error. In those cases, the SE can be computed with simple formulas : SE = CI_95 / t(n), SE = SD/sqrt(n). Those formulas involves the sample size, which can be either the number of individuals or container in toxicology. It was decided to use the individual sample size as it produces larger SE and is thus more conservative. The influence of this decision is examined in a senstivity analysis. 

```{r}

data_CI <- data_CI %>%
  # Creating columns to select the biggest of two CI arms and the individual sample size
  mutate(AI_BIGGEST_CI_ARM = pmax(AI_ERROR_HIGHER, AI_ERROR_LOWER))%>%
  mutate(FORM_BIGGEST_CI_ARM = pmax(FORM_ERROR_HIGHER, FORM_ERROR_LOWER)) %>%
  mutate(AI_N_INDIVIDUAL = AI_N_CONTAINER * AI_N_INDIVIDUALS_PER_CONTAINER) %>%
  mutate(FORM_N_INDIVIDUAL = FORM_N_CONTAINER * FORM_N_INDIVIDUALS_PER_CONTAINER) %>%
  # Calculating the SE from t statistic and sample size
  mutate(AI_SE_INDIVIDUAL = AI_BIGGEST_CI_ARM/(-qt(0.025, df = AI_N_INDIVIDUAL - 1))) %>%
  mutate(FORM_SE_INDIVIDUAL = FORM_BIGGEST_CI_ARM/(-qt(0.025, df = FORM_N_INDIVIDUAL - 1)))
  
```

Same process for SD 

```{r}
data_SD <- data_SD %>%
  # Creating columns for individual sample size
  mutate(AI_N_INDIVIDUAL = AI_N_CONTAINER * AI_N_INDIVIDUALS_PER_CONTAINER) %>%
  mutate(FORM_N_INDIVIDUAL = FORM_N_CONTAINER * FORM_N_INDIVIDUALS_PER_CONTAINER) %>%
  # Calculating the SE from sample size
  mutate(AI_SE_INDIVIDUAL = AI_ERROR_LOWER/sqrt(AI_N_INDIVIDUAL)) %>%
  mutate(FORM_SE_INDIVIDUAL = FORM_ERROR_LOWER/sqrt(FORM_N_INDIVIDUAL))
```

Combining all types of error together

```{r}
data_SE <- data_SE %>%
  # Adding the same columns than the other dataframes
  mutate(AI_N_INDIVIDUAL = AI_N_CONTAINER * AI_N_INDIVIDUALS_PER_CONTAINER) %>%
  mutate(FORM_N_INDIVIDUAL = FORM_N_CONTAINER * FORM_N_INDIVIDUALS_PER_CONTAINER) %>%
  mutate(AI_SE_INDIVIDUAL = AI_ERROR_LOWER) %>%
  mutate(FORM_SE_INDIVIDUAL = FORM_ERROR_LOWER)

data_allSE <- bind_rows(data_SE, data_CI, data_SD)
```

Sorting rows with mixed errors, only 1 in this dataset so could be done by hand.

```{r, message=FALSE, warning=FALSE}
mixed_error_rows <- excluded %>%
  filter(REASON_EXCLUSION == "Not_same_error_type")
# There is just one , where the AI is SE and form is CI, but careful if other ones

mixed_error_fixed <- mixed_error_rows %>%
  mutate(AI_N_INDIVIDUAL = AI_N_CONTAINER * AI_N_INDIVIDUALS_PER_CONTAINER) %>%
  mutate(FORM_N_INDIVIDUAL = FORM_N_CONTAINER * FORM_N_INDIVIDUALS_PER_CONTAINER) %>%
  mutate(AI_SE_INDIVIDUAL = AI_ERROR_LOWER) %>%
  mutate(FORM_BIGGEST_CI_ARM = pmax(FORM_ERROR_HIGHER, FORM_ERROR_LOWER)) %>%
  mutate(FORM_SE_INDIVIDUAL = FORM_BIGGEST_CI_ARM/(-qt(0.025, df = FORM_N_INDIVIDUAL - 1)))
  
# Putting it back in the dataset and out from excluded 

data_allSE <- bind_rows(data_allSE, mixed_error_fixed)

excluded <- anti_join(excluded, mixed_error_rows)

```

### Handling the rows with missing error 

#### Consequences of dropping them

The first step is to know how many rows are in the following categories:

1) AI > the FORM
2) FORM > AI
3) AI = FORM

```{r, message=FALSE, warning=FALSE}
# Excluding rows if negative or null error
# Strange way of doing due to the NA handling 

to_exclude <- data_missing_error %>%
  filter((AI_ERROR_LOWER <= 0 & AI_ERROR_HIGHER <= 0) |
          (FORM_ERROR_LOWER <= 0 & FORM_ERROR_HIGHER <= 0))

data_missing_cleaned <- anti_join(data_missing_error, to_exclude)

excluded <- excluded %>%
  bind_rows(to_exclude %>% mutate(REASON_EXCLUSION = "Both_Error_negative_or_null"))

# Removing two effect sizes, according to Guy: where CI was not generated in primary source due to reliability

data_missing_cleaned <- data_missing_cleaned %>%
  filter(!(DATA_ID %in% c(111, 370)))

excluded <- excluded %>%
  bind_rows(data_missing_error %>% filter(DATA_ID %in% c(111, 370)) %>%
              mutate(REASON_EXCLUSION = "CI_not_reliable_primary_source_seeGuy"))

# Counting the rows in each category 

comparison_summary <- data_missing_cleaned %>%
  mutate(comparison = case_when(
    AI_50 > FORM_50 ~ "AI_50 > FORM_50",
    AI_50 < FORM_50 ~ "AI_50 < FORM_50",
    AI_50 == FORM_50 ~ "AI_50 == FORM_50",
    TRUE ~ "Missing or incomparable"
  )) %>%
  count(comparison)

comparison_summary
```

```{r}
# Some checks 
nrow(data_missing_cleaned) + nrow(excluded) + nrow(data_allSE) == nrow(all_data_formatted)
```
For my dataset, the results are the following: 
1) For 93 the AI has a higher ED50 than the FORM.
2) For 11 the FORM has a higher ED50 than the AI.
3) For 19 the AI and FORM have the same ED50.

This means that for the dataset with missing variance values, 75% of effect sizes had an AI with a bigger ED50 than their formulation.

Now let's see in the rest of the dataset. 

```{r}
comparison_summary2 <- data_cleaned %>%
  mutate(comparison = case_when(
    AI_50 > FORM_50 ~ "AI_50 > FORM_50",
    AI_50 < FORM_50 ~ "AI_50 < FORM_50",
    AI_50 == FORM_50 ~ "AI_50 == FORM_50",
    TRUE ~ "Missing or incomparable"
  )) %>%
  count(comparison)

comparison_summary2
```

Of the 448 effect sizes with no missing SE values:

1) For 286 the AI has a higher ED50 than the FORM.
2) For 9 the FORM has a higher ED50 than the AI.
3) For 153 the AI and FORM have the same ED50.

So for the dataset with variance values, 63.8% of effect sizes had an AI with a bigger ED50 than their formulation. This shows that the data with "missing" SE values has a greater proportion of effect sizes with less toxic AIs in comparison to the data with a variance estimate.

#### Converting all errors in CE

```{r}
# Separating into different types of error 
data_missing_only_ci <- data_missing_cleaned %>%
  filter(AI_ERROR_TYPE == "CI_95" | FORM_ERROR_TYPE == "CI_95")

data_missing_only_se <- data_missing_cleaned %>%
  filter(AI_ERROR_TYPE == "SE" | FORM_ERROR_TYPE == "SE")

data_missing_only_sd <- data_missing_cleaned %>%
  filter(AI_ERROR_TYPE == "SD" | FORM_ERROR_TYPE == "SD")

data_missing_both <- data_missing_cleaned %>%
  filter(is.na(FORM_ERROR_TYPE) & is.na(AI_ERROR_TYPE))
```

```{r}
# Checking
nrow(data_missing_only_ci) + nrow(data_missing_only_sd) + nrow(data_missing_only_se) + nrow(data_missing_both) == nrow(data_missing_cleaned)
```


```{r}
data_missing_only_ci <- data_missing_only_ci %>%
    mutate(AI_N_INDIVIDUAL = AI_N_CONTAINER * AI_N_INDIVIDUALS_PER_CONTAINER) %>%
    mutate(FORM_N_INDIVIDUAL = FORM_N_CONTAINER * FORM_N_INDIVIDUALS_PER_CONTAINER) 

# Separating for ai and form, because one of them is NA and the other is not 
data_missing_only_ci_form <- data_missing_only_ci %>%
  filter(FORM_ERROR_TYPE == "CI_95")%>%
  # Creating columns to select the biggest of two CI arms and the individual sample size
  mutate(FORM_BIGGEST_CI_ARM = pmax(FORM_ERROR_HIGHER, FORM_ERROR_LOWER)) %>%
  # Calculating the SE from t statistic and sample size
  mutate(FORM_SE_INDIVIDUAL = FORM_BIGGEST_CI_ARM/(-qt(0.025, df = FORM_N_INDIVIDUAL - 1)))
  
  
data_missing_only_ci_ai <- data_missing_only_ci %>%
  filter(AI_ERROR_TYPE == "CI_95") %>%
  # Creating columns to select the biggest of two CI arms and the individual sample size
  mutate(AI_BIGGEST_CI_ARM = pmax(AI_ERROR_HIGHER, AI_ERROR_LOWER))%>%
  # Calculating the SE from t statistic and sample size
  mutate(AI_SE_INDIVIDUAL = AI_BIGGEST_CI_ARM/(-qt(0.025, df = AI_N_INDIVIDUAL - 1)))

data_missing_only_ci_semifixed <- bind_rows(data_missing_only_ci_form, data_missing_only_ci_ai)
  
```


```{r}
# Doing the same for SD 

data_missing_only_sd <- data_missing_only_sd %>%
    mutate(AI_N_INDIVIDUAL = AI_N_CONTAINER * AI_N_INDIVIDUALS_PER_CONTAINER) %>%
    mutate(FORM_N_INDIVIDUAL = FORM_N_CONTAINER * FORM_N_INDIVIDUALS_PER_CONTAINER) 

# Separating for ai and form, because one of them is NA and the other is not 
data_missing_only_sd_form <- data_missing_only_sd %>%
  filter(FORM_ERROR_TYPE == "SD")%>%
  # Calculating the SE from sample size
  mutate(FORM_SE_INDIVIDUAL = FORM_ERROR_LOWER/sqrt(FORM_N_INDIVIDUAL))
  
  
data_missing_only_sd_ai <- data_missing_only_sd %>%
  filter(AI_ERROR_TYPE == "SD") %>%
  # Calculating the SE from sample size
  mutate(AI_SE_INDIVIDUAL = AI_ERROR_LOWER/sqrt(AI_N_INDIVIDUAL))

data_missing_only_sd_semifixed <- bind_rows(data_missing_only_sd_form, data_missing_only_sd_ai)
```

```{r}
# Rejoining all the types of error 

data_missing_only_se_semifixed <- data_missing_only_se %>%
  # Adding the same columns than the other dataframes
  mutate(AI_N_INDIVIDUAL = AI_N_CONTAINER * AI_N_INDIVIDUALS_PER_CONTAINER) %>%
  mutate(FORM_N_INDIVIDUAL = FORM_N_CONTAINER * FORM_N_INDIVIDUALS_PER_CONTAINER) %>%
  mutate(AI_SE_INDIVIDUAL = AI_ERROR_LOWER) %>%
  mutate(FORM_SE_INDIVIDUAL = FORM_ERROR_LOWER)

data_missing_both <- data_missing_both %>%
  # Adding the same columns than the other dataframes
  mutate(AI_N_INDIVIDUAL = AI_N_CONTAINER * AI_N_INDIVIDUALS_PER_CONTAINER) %>%
  mutate(FORM_N_INDIVIDUAL = FORM_N_CONTAINER * FORM_N_INDIVIDUALS_PER_CONTAINER) %>%
  mutate(AI_SE_INDIVIDUAL = AI_ERROR_LOWER) %>%
  mutate(FORM_SE_INDIVIDUAL = FORM_ERROR_LOWER)  

# Combining
data_missing_error_semifixed <- bind_rows(data_missing_only_ci_semifixed, data_missing_only_sd_semifixed, data_missing_only_se_semifixed, data_missing_both)

data_cleaned_not_imputed <- bind_rows(data_allSE, data_missing_error_semifixed) %>%
  arrange(DATA_ID)
```

```{r}
# Check 
nrow(data_cleaned_not_imputed) + nrow(excluded) == nrow(all_data_formatted)
```

### Computing the log ratio 


Now we can calculate the ln(response ratio) and variance for each. Traditionally, LRR = ln(Xt/Xc). This means that a negative sign shows the formulation is more toxic.

```{r}
data_cleaned_not_imputed <- data_cleaned_not_imputed %>%
  # Calculating LRR
  mutate(LRR = log(FORM_50/AI_50)) %>%
  # Calculating LRR variance using delta method : var(lnRR) = SE_FORM^2/mean_FORM^2 + SE_AI^2/mean_AI^2
  mutate(LRR_VAR_INDIVIDUAL = (FORM_SE_INDIVIDUAL^2 / FORM_50^2) + (AI_SE_INDIVIDUAL^2 / AI_50^2))
   
```


### Some visualizations 

Let's visualize the distribution of log ratio and check the normality. 

```{r}
ggplot(data_cleaned_not_imputed, aes(x = LRR))+
  geom_histogram(bins = 50, fill = "green", colour = "black", alpha = 0.5) + 
  xlab("Log Response Ratio")+
  ylab("Histogram")+
  theme_bw()
```

Now we look into the distribution of missing SE compared to the other rows: are they associated with higher TDDs? 

```{r}
# Getting the data in a simple, long format 
vis <- data_cleaned_not_imputed %>%
  dplyr::select(AI_50, AI_SE_INDIVIDUAL, FORM_50, FORM_SE_INDIVIDUAL) %>%
  pivot_longer(
    cols = everything(),
    names_to = c("Treatment", ".value"),
    names_pattern = "(AI|FORM)_(50|SE_INDIVIDUAL)"
  ) %>%
  rename(TDD = `50`, SE = SE_INDIVIDUAL) %>%
  mutate(MISSING = is.na(SE))

# Visualising the two densities, filtering otherwise we cannot see 

ggplot(vis %>% filter(TDD < 1000), aes(x = TDD, fill = as.factor(MISSING))) +
  geom_density(alpha = 0.5) +
  xlab("TDD < 1000") +
  ylab("Density") +
  theme_bw()+ 
    scale_fill_manual(
    values = c("FALSE" = "pink", "TRUE" = "turquoise"),
    labels = c("FALSE" = "Not missing", "TRUE" = "Missing"),
    name = NULL  # removes the legend title
  ) +
  theme(legend.position.inside = c(0.8,0.8))
```


### Adding a simple time variable 

Need to create a false unit of time in order to model the dependance between effect sizes coming from multiple measurements. 

```{r}
data_cleaned_not_imputed <- data_cleaned_not_imputed %>%
  group_by(MULTIPLE_MEASUREMENT) %>%
  arrange(MULTIPLE_MEASUREMENT, EXPOSURE_DURATION_HOURS) %>%
  mutate(TIME_SIMPLE = row_number()) %>%
  ungroup()
```


### Excluding problematic data 


```{r}
# Saving for after 
data_everybody_before_exclusions <- data_cleaned_not_imputed
```

#### Error too big 

Rows where the SE is 10 times bigger than the value are excluded. The effect of those exclusions is explored in a sensitivity analysis. 

```{r, message=FALSE, warning=FALSE}
to_exclude <- data_cleaned_not_imputed %>%
  filter(AI_SE_INDIVIDUAL > AI_50*10 | FORM_SE_INDIVIDUAL > FORM_50*10)

excluded <- excluded %>%
  bind_rows(to_exclude %>% 
              mutate(REASON_EXCLUSION = "Error_supp_10_times_value"))

data_cleaned_not_imputed <- anti_join(data_cleaned_not_imputed, to_exclude)
```


####  Phylogenetic independance

Effect sizes derived from cell lines and microbial community need to be excluded for now because we need to calculate a phylogenetic covariance term for the model selection. For the same reason, taxon that cannot be resolved in the open tree of life are excluded. 

```{r, message=FALSE, warning=FALSE}
to_exclude <- data_cleaned_not_imputed %>%
  filter(is.na(SPECIES_NAME_BINOMIAL))

excluded <- excluded %>%
  bind_rows(to_exclude %>%
              mutate(REASON_EXCLUSION = "microbial_or_cells"))

data_cleaned_not_imputed <- anti_join(data_cleaned_not_imputed, to_exclude)
```

```{r, message=FALSE, warning=FALSE}
taxa <- unique(data_cleaned_not_imputed$SPECIES_NAME_BINOMIAL)

# resolves names. A few of the names were older synonyms
resolved_names <- tnrs_match_names(taxa)

# Two taxa are not in the tree of life so I'll remove them for now 

to_exclude_names <- resolved_names %>%
  filter(flags %in% c("hidden", "incertae_sedis")) %>%
  distinct(unique_name) %>%
  mutate(first_two = word(unique_name, 1, 2)) # because some rows have additionnal info in unique name 
  

to_exclude <- data_cleaned_not_imputed %>%
  filter(SPECIES_NAME_BINOMIAL %in% to_exclude_names$first_two)
  

excluded <- excluded %>%
  bind_rows(to_exclude %>% mutate(REASON_EXCLUSION = "Name_not_in_open_tree"))

# Saving for after
data_before_exclusions_decisions <- data_cleaned_not_imputed

data_cleaned_not_imputed <- anti_join(data_cleaned_not_imputed, to_exclude)


```


#### One study only 

In this dataset, there are only 1 study for the pesticide class algaecide and anti-parasitic, so  excluding them, there is no interest to do a meta-analysis on one study

```{r, warning = FALSE, message = FALSE}
# Look at the number of studies per class of moderators
mod_number <- data_cleaned_not_imputed %>%
  count(PESTICIDE_CLASS, name = "Number")

to_exclude <- data_cleaned_not_imputed %>%
  filter(PESTICIDE_CLASS %in% c("algaecide", "anti-parasitic"))

excluded <- excluded %>%
  bind_rows(to_exclude %>% mutate(REASON_EXCLUSION = "Sole_study_per_moderator"))

data_cleaned_not_imputed <- anti_join(data_cleaned_not_imputed, to_exclude)
```

#### Influential effect sizes

Effect sizes that can indivudually affect the significance of one class are excluded. This comes from the leave1out analysis that is presented later in the markdown because it needs the model. The leave1out analysis takes a really long time to run (2h), so only the results are presented. If you want to do it yourself, don't run this chunk (because the influential will already be excluded).

```{r}
influential_to_exclude <- read_csv("output/leave1out_to_exclude.csv")

excluded <- excluded %>%
  bind_rows(influential_to_exclude %>% mutate(REASON_EXCLUSION = "Influential"))

data_cleaned_not_imputed <- data_cleaned_not_imputed %>%
  filter(!DATA_ID %in% influential_to_exclude$DATA_ID )

```

```{r}
# Check 
nrow(excluded) + nrow(data_cleaned_not_imputed) == nrow(all_data)
```


## Chosing the model 

This steps are done on the dataset without missing errors, because we need a model in order to impute the missing errors. There will also be exclusions/reintroductions after the leave one out and sensitivity analysis, but, as both also necessitates a working model, the model selection has to be done on the reduced dataset. It will be verified once the dataset is final. 

### Non indepedance in the dataset 

#### Error Covariance matrices

As this dataset presents complex form of non independence, it is necessary to correctly model them. First, we want to account for the covariance between errors of effect sizes. We've identified three sources: shared controls (two formulations for one ai), repeated measurements in time (LC50 at 24 and 48H) and repeated measurements with different methods (biomass and chlorphyl content for algae can be used to compute an LC50). If the CONTROL_GROUP, TEST_GROUP, MULTIPLE_MEASUREMENT and MULTIPLE_TYPE columns are correctly filled, it is possible to use vcalc function in metafor to compute a covariance matrix accounting for all of this.

```{r}
# Separating again into missing/no_missing

data_cleaned_no_missing <- data_cleaned_not_imputed %>%
   filter(SE_SIMULATION_REQUIRED == "NO")

data_cleaned_with_missing <- data_cleaned_not_imputed %>%
  filter(SE_SIMULATION_REQUIRED == "YES")


# Correlation matrix

autocorrelation_matrix <- metafor::vcalc(vi = LRR_VAR_INDIVIDUAL,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_N_INDIVIDUAL,
               w2 = FORM_N_INDIVIDUAL,
               time1 = TIME_SIMPLE,
               phi = 0.8,
               rho = 0.8,
               data= data_cleaned_no_missing)



# visualise the correlation
# Set the chunk size (e.g., 50 rows/columns at a time)
chunk_size <- 50
n <- nrow(autocorrelation_matrix)

# Loop through chunks and plot each
for (i in seq(1, n, by = chunk_size)) {
  end <- min(i + chunk_size - 1, n)
  corrplot(cov2cor(autocorrelation_matrix[i:end, i:end]))
}




```

```{r}
# Saving nice examples of the matrix 

data_before_decisions_nm <- data_before_exclusions_decisions %>%
   filter(SE_SIMULATION_REQUIRED == "NO")

# Correlation matrix

autocorrelation_matrix_decisions <- metafor::vcalc(vi = LRR_VAR_INDIVIDUAL,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_N_INDIVIDUAL,
               w2 = FORM_N_INDIVIDUAL,
               time1 = TIME_SIMPLE,
               phi = 0.8,
               rho = 0.8,
               data= data_before_decisions_nm)



# visualise the correlation
# Set the chunk size (e.g., 50 rows/columns at a time)
chunk_size <- 50
n <- nrow(autocorrelation_matrix_decisions)

# Loop through chunks and plot each
for (i in seq(1, n, by = chunk_size)) {
  end <- min(i + chunk_size - 1, n)
  corrplot(cov2cor(autocorrelation_matrix_decisions[i:end, i:end]))
}

# Creating a list for plotting 
Vs <- blsplit(autocorrelation_matrix_decisions, data_before_decisions_nm$STUDY_ID)


# Saving interesting examples (wos1565, 868, 271)
cairo_pdf("output/example_covariance_matrix.pdf")
corrplot::corrplot(cov2cor(Vs[[41]]))
corrplot::corrplot(cov2cor(Vs[[12]])) 
corrplot::corrplot(cov2cor(Vs[[7]]))
dev.off()
```


#### Phylogenetic covariance

We have to construct a term accounting for evolutionary relatedness

```{r, warning=FALSE}

# Re-doing the taxa names
taxa2 <- unique(data_cleaned_no_missing$SPECIES_NAME_BINOMIAL)

# resolves names. A few of the names were older synonyms
resolved_names2 <- tnrs_match_names(taxa2)

my_tree <- tol_induced_subtree(ott_ids = resolved_names2$ott_id, label_format = "name")

plot(my_tree, type = "phylogram", cex = 0.3)

# Adding the updated names to the data 

# Creating a function that capitalizes the first letter 
capitalize_first <- function(x) {
  paste0(toupper(substr(x, 1, 1)), tolower(substr(x, 2, nchar(x))))
}

# creating a column in resolve name with only two words for the name 
update_name <- resolved_names2 %>%
  mutate(SPECIES_NAME_BINOMIAL_OTL = unique_name) %>%
  mutate(SPECIES_NAME_BINOMIAL = capitalize_first(search_string)) %>%
  dplyr::select(SPECIES_NAME_BINOMIAL, SPECIES_NAME_BINOMIAL_OTL)


#  Join the updated names into the full data
data_cleaned_no_missing <- data_cleaned_no_missing %>%
  left_join(update_name, by = "SPECIES_NAME_BINOMIAL") 

# Adding a _

data_cleaned_no_missing <- data_cleaned_no_missing %>%
  mutate(SPECIES_NAME_BINOMIAL_OTL = str_replace_all(SPECIES_NAME_BINOMIAL_OTL, " ", "_"))
```

```{r}
# Check: is there a match between tree tips labels and names in the dataset 

tree_tip_label <- my_tree$tip.label
diff <- setdiff(tree_tip_label, data_cleaned_no_missing$SPECIES_NAME_BINOMIAL_OTL) 
diff
```

```{r}
# calculate branch lengths
my_tree <- ape::compute.brlen(my_tree, method = "Grafen", power = 1)

# use a randomization approach to deal with polytomies
my_tree <- ape::multi2di(my_tree, random = TRUE)

# create correlation matrix for analysis
phylo_cor <- vcv(my_tree, cor = T)

# save species tree
cairo_pdf("output/species_tree_plot.pdf")
plot(my_tree, type = "phylogram", cex = 0.3)
dev.off()
```

###  Forward selection for random effects 

Now that we have created the correct terms, we will use forward selection to determine which random effects are adding to the model. The list of potential random effects is the following: 

1) ~1 | STUDY (between study variation)

2) ~1 | DATA_ID (within study variation (residual variance))

3) ~1 | SPECIES_NAME_BINOMIAL_OTL (control for evolutionary relatedness. For example, co-formulants are expected to affect two species of water flea more similarly than a bacteria due to more similar molecular and cellular targets, due to a shared evolutionary history)

4) ~1 | SPECIES_NAME_BINOMIAL (the non-phylogenetic relatedness, this controls for ecological similarities like being both aquatic. Failing to include this term will often inflate the phylogenetic variance)

5) TIME | MULTIPLE_MEASUREMENT, struct = "AR". This is a compromise between using a simple random effect of time and allowing the time to be not evenly spaced. 

we are starting with a NULL model with all the potential fixed effects and the autocorrelation vcv matrix. The significance is determined by looking at the AIC difference and the p value using the anova function.

#### Round 1: Comparing null model to individual random effects 

```{r, warning=FALSE}
# NULL model
null_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                    data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")
```

Adding random effects one by one and testing their significance
```{r, warning=FALSE}
# ROUND 1
# add STUDY_ID as random effect
study_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                    random = list(~1 | STUDY_ID),
                    data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")

# STUDY_ID is significant
anova.rma(null_mod, study_mod)
```

```{r, warning=FALSE}
# add DATA_ID as a random effect
es_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                    random = list(~1 | DATA_ID),
                    data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")

# DATA_ID is significant
anova.rma(null_mod, es_mod)
```

```{r, warning=FALSE}
# phylogenetic species term SPECIES_NAME_BINOMIAL_OTL
phylo_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                    random = list(~1 | SPECIES_NAME_BINOMIAL_OTL),
                    R = list(SPECIES_NAME_BINOMIAL_OTL = phylo_cor),
                    data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")

# the phylogenetic structure is significant
anova.rma(null_mod, phylo_mod)
```

```{r, warning=FALSE}
# non-phylogenetic species term SPECIES_NAME_BINOMIAL_OTL
species_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                    random = list(~1 | SPECIES_NAME_BINOMIAL_OTL),
                    data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")

# significant
anova.rma(null_mod, species_mod)
```

```{r, warning=FALSE}
# SIMPLE_TIME | MULTIPLE_MEASUREMENT term
ar_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                 mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                 random = list(~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                 struct = "AR",
                 data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")

# significant
anova.rma(null_mod, ar_mod)
```

#### Round 2 : Compare random effect to the model accounting for multiple measurements 

```{r, warning=FALSE}
# ROUND 2, AR is now the reference
# AR + DATA_ID. MULTIPLE_MEASUREMENT has replaced DATA_ID really.
# all moderators are either at study level or multiple_measurement level (apart from TIME_SIMPLE)
ar_es_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                 mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                 random = list(~1 | DATA_ID,
                               ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                 struct = "AR",
                 data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")

# Not significant
anova.rma(ar_mod, ar_es_mod)
```

```{r, warning=FALSE}
# AR + STUDY_ID
ar_study_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                 mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                 random = list(~1 | STUDY_ID,
                               ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                 struct = "AR",
                 data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")

# significant
anova.rma(ar_mod, ar_study_mod)
```

```{r, warning=FALSE}
# AR + phylo
ar_phylo_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                 mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                 random = list(~1 | SPECIES_NAME_BINOMIAL_OTL,
                               ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                 R = list(SPECIES_NAME_BINOMIAL_OTL = phylo_cor),
                 struct = "AR",
                 data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")

# slihtly not significant 
anova.rma(ar_mod, ar_phylo_mod)
```

```{r, warning=FALSE}
# AR + species
ar_species_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                 mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                 random = list(~1 | SPECIES_NAME_BINOMIAL_OTL,
                               ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                 struct = "AR",
                 data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")

# significant
anova.rma(ar_mod, ar_species_mod)
```

#### Round 3
```{r, warning=FALSE}
# ROUND 3 AR + STUDY_ID now reference
# AR + study + phylo
ar_study_phylo_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                 mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                 random = list(~1 | STUDY_ID,
                               ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT,
                               ~1 | SPECIES_NAME_BINOMIAL_OTL),
                 R = list(SPECIES_NAME_BINOMIAL_OTL = phylo_cor),
                 struct = "AR",
                 data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")

# not significant
anova(ar_study_mod, ar_study_phylo_mod)
```

```{r, warning=FALSE}
# AR + study + species
ar_study_species_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                 mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                 random = list(~1 | STUDY_ID,
                               ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT,
                               ~1 | SPECIES_NAME_BINOMIAL_OTL),
                 struct = "AR",
                 data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")

# not significant
anova(ar_study_mod, ar_study_species_mod)
```

```{r, warning=FALSE}
# AR + study + data ID
ar_study_data_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                 mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                 random = list(~1 | STUDY_ID,
                               ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT,
                               ~1 | DATA_ID),
                 struct = "AR",
                 data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")

# Not significant
anova(ar_study_mod, ar_study_data_mod)
```


#### Results 



```{r, warning=FALSE}
# this is the final model in relation to the random effects
ar_study_data_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                 mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                 random = list(~1 | STUDY_ID,
                               ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                 struct = "AR",
                 data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")

summary(ar_study_data_mod)
```



### Backward selection predictors

Now we will select the moderators using backward selection. We start with the full model and drop predictors if they don't add significant improvement to the model. 

```{r}
# Simplyfing the EXPOSURE_ROUTE column 
data_cleaned_no_missing <- data_cleaned_no_missing %>%
  mutate(EXPOSURE_ROUTE = case_when(
    EXPOSURE_ROUTE %in% c("oral-gavage", "oral-food", "oral-proventriculus") ~ "oral",
    TRUE ~ EXPOSURE_ROUTE
  ))
```


```{r, warning=FALSE}
# express the reference model using ML
ar_study_data_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                    random = list(~1 | STUDY_ID,
                                  ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                    struct = "AR",
                    data = data_cleaned_no_missing, method = "ML", test = "t", dfs = "contain")
```

First we look at the collinearity between moderators, which is quite high. 

```{r, warning=FALSE}
# GVIF to check for collinearity between moderators. Cutoff of 5 or 10 are sometimes used.
vif(ar_study_data_mod, btt = c("PESTICIDE_CLASS", "EXPOSURE_ROUTE", "FORMULATION_TYPE"))
```

#### Round 0: Interactions

```{r, warning=FALSE}
# Testing for the interaction between pesticide class and formulation type 
ar_study_data_mod_int <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE +
                      PESTICIDE_CLASS:FORMULATION_TYPE,
                    random = list(~1 | STUDY_ID,
                                  ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                    struct = "AR",
                    data = data_cleaned_no_missing, method = "ML", test = "t", dfs = "contain")

anova(ar_study_data_mod, ar_study_data_mod_int)
# Not significant, dropping the interaction term 
```




#### Round 1: Full vs 2 predictors

```{r, warning=FALSE}
# backward selection for the fixed effect 

ar_study_data_mod_a <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE,
                    random = list(~1 | STUDY_ID,
                                  ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                    struct = "AR",
                    data = data_cleaned_no_missing, method = "ML", test = "t", dfs = "contain")

ar_study_data_mod_b <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ PESTICIDE_CLASS + FORMULATION_TYPE,
                    random = list(~1 | STUDY_ID,
                                  ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                    struct = "AR",
                    data = data_cleaned_no_missing, method = "ML", test = "t", dfs = "contain")

ar_study_data_mod_c <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ EXPOSURE_ROUTE + FORMULATION_TYPE,
                    random = list(~1 | STUDY_ID,
                                  ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                    struct = "AR",
                    data = data_cleaned_no_missing, method = "ML", test = "t", dfs = "contain")
```


```{r, warning=FALSE}
anova(ar_study_data_mod, ar_study_data_mod_a)
# Not significant 
```

```{r, warning=FALSE}
anova(ar_study_data_mod, ar_study_data_mod_b)
# Not significant 
```

```{r, warning=FALSE}
anova(ar_study_data_mod, ar_study_data_mod_c)
# Significant 
```

We can see that dropping PESTICIDE CLASS worsens the fits 

#### Round 2: Pesticide class vs 2 predictors 

```{r, warning=FALSE}
# 
ar_study_data_mod_pest <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ PESTICIDE_CLASS,
                    random = list(~1 | STUDY_ID,
                                  ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                    struct = "AR",
                    data = data_cleaned_no_missing, method = "ML", test = "t", dfs = "contain")
```

```{r, warning=FALSE}
anova(ar_study_data_mod_pest, ar_study_data_mod_b)
# Not significant 
```

```{r, warning=FALSE}
anova(ar_study_data_mod_pest, ar_study_data_mod_a)
# Not significant 
```

#### Round 3: Null model 

```{r, warning=FALSE}
# ar_study_data_mod_pest is the reference
ar_study_data_mod_null <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ 1,
                    random = list(~1 | STUDY_ID,
                                  ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                    struct = "AR",
                    data = data_cleaned_no_missing, method = "ML", test = "t", dfs = "contain")

anova(ar_study_data_mod_pest, ar_study_data_mod_null)
# Significant 
```

So the final model only comprises PESTICIDE_CLASS as a moderator. We've done it by hand, but we can compare with the automatic version. 

```{r, warning=FALSE}
# Comparing with the selection using MuMin

eval(metafor:::.MuMIn) # use eval() function to extract helper functions from MuMIn and make them usable in metafor.

mod.candidate <- dredge(ar_study_data_mod, beta = "none", evaluate = TRUE, rank = "AICc", trace=2) # dredge to produce all possible models

# same as manual selection
subset(mod.candidate, delta <= 2, recalc.weights = FALSE)
```

However, the FORMULATION_TYPE moderator has currently a lot of "liquid formulation", which means that the formulation type was not detailed. We are re-running the selection on a reduced dataset without the unsure formulations. 

```{r}
# Replacing liquid formulation and unsure by NAs
data_cnm_form_adjusted <- data_cleaned_no_missing %>%
  mutate(FORMULATION_TYPE = na_if(FORMULATION_TYPE, "liquid formulation")) %>%
  mutate(FORMULATION_TYPE = na_if(FORMULATION_TYPE, "unsure")) %>%
  drop_na(FORMULATION_TYPE)

autocorrelation_matrix2 <- metafor::vcalc(vi = LRR_VAR_INDIVIDUAL,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_N_INDIVIDUAL,
               w2 = FORM_N_INDIVIDUAL,
               time1 = TIME_SIMPLE,
               phi = 0.8,
               rho = 0.8,
               data= data_cnm_form_adjusted)

ar_study_data2_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix2,
                    mod = ~ PESTICIDE_CLASS + EXPOSURE_ROUTE + FORMULATION_TYPE,
                    random = list(~1 | STUDY_ID,
                                  ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                    struct = "AR",
                    data = data_cnm_form_adjusted, method = "ML", test = "t", dfs = "contain")
```

```{r}
eval(metafor:::.MuMIn) # use eval() function to extract helper functions from MuMIn and make them usable in metafor.

mod.candidate <- dredge(ar_study_data2_mod, beta = "none", evaluate = TRUE, rank = "AICc", trace=2) # dredge to produce all possible models

# same as manual selection
subset(mod.candidate, delta <= 2, recalc.weights = FALSE)
```

This also results in PESTICIDE_CLASS being the only significant moderator. 

This means that the final model is the following: 

```{r, warning=FALSE}
# Final model with REML
final_model_reml <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ 0 + PESTICIDE_CLASS,
                    random = list(~1 | STUDY_ID,
                                  ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                    struct = "AR",
                    data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")
```


Now we can compare the estimates of our model with the ones from the RVE, to see if our structure is relevant. 

```{r}

# RVE
robust(final_model_reml, cluster = data_cleaned_no_missing$STUDY_ID, clubSandwich = TRUE)

# PIs
mod_results(final_model_reml, group = "STUDY_ID", mod = "PESTICIDE_CLASS")$mod_table


```

The estimates are really close so our dependance structure looks relevant. 

The final model in terms of random effects does not include the term linked to the phylogenetic covariance. As a result, it was decided to reintegrate the effect sizes that were excluded because they didn't fit in the phylogenetic computation. 

```{r, message=FALSE, warning=FALSE}
phylo_excluded <- excluded %>%
  filter(REASON_EXCLUSION %in% c("microbial_or_cells", "Name_not_in_open_tree"))
  
phylo_excluded_no_missing <- phylo_excluded %>%
  filter(SE_SIMULATION_REQUIRED == "NO")

phylo_excluded_se_missing <- phylo_excluded %>%
  filter(SE_SIMULATION_REQUIRED == "YES")

data_cleaned_no_missing_wt_phylo <- data_cleaned_no_missing
data_cleaned_no_missing <- bind_rows(data_cleaned_no_missing, phylo_excluded_no_missing) 

data_cleaned_not_imputed_wt_phylo <- data_cleaned_not_imputed 
data_cleaned_with_missing_wt_phylo <- data_cleaned_with_missing
data_cleaned_not_imputed <- bind_rows(data_cleaned_not_imputed, phylo_excluded) 
data_cleaned_with_missing <- bind_rows(data_cleaned_with_missing, phylo_excluded_se_missing)

excluded <- anti_join(excluded, phylo_excluded)
```


```{r}
autocorrelation_matrix <- metafor::vcalc(vi = LRR_VAR_INDIVIDUAL,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_N_INDIVIDUAL,
               w2 = FORM_N_INDIVIDUAL,
               time1 = TIME_SIMPLE,
               phi = 0.8,
               rho = 0.8,
               data= data_cleaned_no_missing)

# Final model with REML
final_model_reml <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ 0 + PESTICIDE_CLASS,
                    random = list(~1 | STUDY_ID,
                                  ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                    struct = "AR",
                    data = data_cleaned_no_missing, method = "REML", test = "t", dfs = "contain")

# Plot 

final_model_plot <- orchard_plot(final_model_reml, 
                                         mod = "PESTICIDE_CLASS", 
                                         xlab = "Effect size lnRR", 
                                         group = "STUDY_ID",  k = TRUE, g = TRUE, trunk.size = 1.5) +
  scale_fill_manual(values = c("violetred3","yellowgreen", "goldenrod1") ) +
  scale_colour_manual(values = c("violetred3","yellowgreen", "goldenrod1"))


final_model_plot
```

#### Defining a function to get estimates from a model 

```{r}
# Define a function that gets a line of estimates from a model 
estim_mod_wide <- function(mod, name){
  # Extract the values from the model 
  large_df <- data.frame(
  PESTICIDE_CLASS = gsub("^PESTICIDE_CLASS", "", rownames(mod$beta)), # So that column names are identical
  estimate = as.vector(mod$beta),
  lower = mod$ci.lb,
  upper = mod$ci.ub
) %>%
  mutate(model = name) %>%
  dplyr::select(model, PESTICIDE_CLASS, estimate, lower, upper)
  
  # Put it in wide format 
  wide_df <- large_df %>%
  pivot_wider(
    names_from = PESTICIDE_CLASS,
    values_from = c(estimate, lower, upper)) %>%
  mutate(across(-model, \(x) round(x, digits = 4)))
  
  # Order the columns
  # Get pesticide names from column suffixes
  pesticides <- sub(".*_(.*)", "\\1", grep("^estimate_", names(wide_df), value = TRUE))
  
  # Build the desired column order
  ordered_cols <- c("model", unlist(lapply(pesticides, function(p) {
    c(paste0("estimate_", p), paste0("lower_", p), paste0("upper_", p))
  })))
  
  # Reorder columns
  wide_ordered <- wide_df[, ordered_cols]
    
  
  return(wide_ordered)
} 
```


```{r}
est_final <- estim_mod_wide(final_model_reml, "Without imputation")
```

```{r}
# RVE
robust(final_model_reml, cluster = data_cleaned_no_missing$STUDY_ID, clubSandwich = TRUE)

# PIs
mod_results(final_model_reml, group = "STUDY_ID", mod = "PESTICIDE_CLASS")$mod_table

```


## Imputation of missing SE data 

As we've seen that the missing data could be important for the outcome, the aim is to find a method to impute the missing SE and then use the full dataset. 

### First method 

The first method is to use a gamma distribution of SE/TDD to draw the missing errors, repeat it 100 times and use the median model. 

#### Relationship between SE and TDD

```{r}
# First we will try to fit a relationship between SE and TDD

# Putting the datasets in long format 
data_long_no_missing <- data_cleaned_not_imputed %>%
  filter(!is.na(AI_ERROR_TYPE)) %>%
  mutate(TDD = AI_50,
         SE = AI_SE_INDIVIDUAL,
         AI_FORM = "AI") %>%
  dplyr::select(DATA_ID, TDD, SE, AI_FORM) %>%
  bind_rows(data_cleaned_not_imputed %>%
              filter(!is.na(FORM_ERROR_TYPE))%>%
              mutate(TDD = FORM_50,
                    SE = FORM_SE_INDIVIDUAL,
                    AI_FORM = "FORM") %>%
              dplyr::select(DATA_ID, TDD, SE, AI_FORM))

data_long_missing <- data_cleaned_not_imputed %>%
  filter(is.na(AI_ERROR_TYPE)) %>%
  mutate(TDD = AI_50,
         SE = AI_SE_INDIVIDUAL,
         AI_FORM = "AI") %>%
  dplyr::select(DATA_ID, TDD, SE, AI_FORM) %>%
  bind_rows(data_cleaned_not_imputed %>%
              filter(is.na(FORM_ERROR_TYPE))%>%
              mutate(TDD = FORM_50,
                    SE = FORM_SE_INDIVIDUAL,
                    AI_FORM = "FORM") %>%
              dplyr::select(DATA_ID, TDD, SE, AI_FORM))
  
# Check:
n_missing_se <- data_cleaned_not_imputed %>%
  summarise(
    n_missing = sum(is.na(FORM_ERROR_TYPE)) + sum(is.na(AI_ERROR_TYPE))
  )%>%
  pull()

# Plotting the relationship between SE and ED50

ggplot(data_long_no_missing, aes(x = TDD, y = SE))+
  geom_point()+
  theme_bw()

# Zoom in

zoomed_plot <- ggplot(data_long_no_missing, aes(x = TDD, y = SE)) +
  geom_point(shape = 21, color = "black", size = 2) +  # Circle points
  xlim(0, 2000) +
  ylim(0, 200) +
  xlab("TDD < 2000")+
  ylab("SE < 200") + 
  theme_bw() +
  theme(
    panel.grid = element_blank()  # Removes all grid lines
  )

zoomed_plot

cairo_pdf("output/se_tdd_relationship.pdf")
zoomed_plot
dev.off()
```

In this plot, SE seems to increase with the TDD. This means that the data that we want to impute is not random, because it is the highest value tested, so tend to be in the higher TDDs. As a result, we use the ratio SE/TDD. It also makes it unitless. 

```{r}
data_long_no_missing <- data_long_no_missing %>%
  mutate(SE_PROP_ED_50 = SE/TDD)

# Plotting 

prop_zoomed_plot <- ggplot(data_long_no_missing %>%
         filter(TDD < 2000 & SE_PROP_ED_50 < 5), aes(x = TDD, y = SE_PROP_ED_50)) + 
    geom_point(shape = 21, color = "black", size = 2) +  # Circle points
  xlim(0, 2000) +
  ylim(0, 5) +
  xlab("TDD < 2000")+
  ylab("SE/TDD < 5 ") +
  theme_bw() +
  theme(
    panel.grid = element_blank()  # Removes all grid lines
  )

prop_zoomed_plot

cairo_pdf("output/se_prop_tdd_tdd_plot.pdf")
prop_zoomed_plot
dev.off()

# Plotting the distribution od se as a proportion of mean distribution
ggplot(data_long_no_missing, aes(x = SE_PROP_ED_50)) +
  geom_density() +
  xlab("SE/TDD") +
  ylab("Density")+
  theme_bw()


ggplot(data_long_no_missing %>%
         filter(SE_PROP_ED_50 < 1), aes(x = SE_PROP_ED_50)) +
  geom_density() +
  xlab("SE/TDD < 1") +
  ylab("Density")+
  theme_bw()


# Fitting a gamma distribution

# Using < 1 allows for a more precise fitting and is actually more conservative 
SE_PROP_ED_50_gamma <- fitdist(((data_long_no_missing%>%
         filter(SE_PROP_ED_50 < 1))$SE_PROP_ED_50),
               distr = "gamma",
               method = "mle")

summary(SE_PROP_ED_50_gamma)

plot(SE_PROP_ED_50_gamma)
```


```{r}
# how many SEs need to be imputed?
n_missing_se

# Simulate a drawing
SE_PROP_ED_50_gamma_imputation <- rgamma(n = n_missing_se, shape = SE_PROP_ED_50_gamma$estimate [[1]], rate = SE_PROP_ED_50_gamma$estimate [[2]])

min(SE_PROP_ED_50_gamma_imputation)
max(SE_PROP_ED_50_gamma_imputation)
```


```{r}
# Define a function that fits the distrib, assign the values, calculate the model 

imputing <- function(data_missing, data_full, distrib) {
  # Data missing needs to be in a long format, wih SE, TDD, AI_FORM as columns
  n_missing <- nrow(data_missing)
  draw_values <- rgamma(n = n_missing, shape = distrib$estimate[[1]], rate = distrib$estimate[[2]])
  
  data_missing <- data_missing %>%
    mutate(SE = TDD * draw_values)
  
  # Split and assign
  AI_data <- data_missing %>% filter(AI_FORM == "AI")
  FORM_data <- data_missing %>% filter(AI_FORM == "FORM")
  
  data_imputed <- data_full %>%
    mutate(
      AI_SE_INDIVIDUAL = ifelse(is.na(AI_SE_INDIVIDUAL), AI_data$SE, AI_SE_INDIVIDUAL),
      AI_ERROR_TYPE = ifelse(is.na(AI_ERROR_TYPE), "imputed", AI_ERROR_TYPE),
      FORM_SE_INDIVIDUAL = ifelse(is.na(FORM_SE_INDIVIDUAL), FORM_data$SE, FORM_SE_INDIVIDUAL),
      FORM_ERROR_TYPE = ifelse(is.na(FORM_ERROR_TYPE), "imputed", FORM_ERROR_TYPE)
    )
  
  data_imputed <- data_imputed %>%
    mutate(LRR_VAR_INDIVIDUAL = (FORM_SE_INDIVIDUAL^2 / FORM_50^2) + (AI_SE_INDIVIDUAL^2 / AI_50^2))
  
  
  return(data_imputed)
}


```

This will take a long time to run, so it is commented and the results have been saved in the outputs


```{r}
# # Running 100 times
# n_run <- 100
# # Preparing empty containers
# imputed_data <- vector("list", n_run)
# imputed_model <- vector("list", n_run)
# imputed_vcv <- vector("list", n_run)
# imputed_estimates <- tibble()
# 
# # For loop a 100 times
# for (i in 1:n_run){
#   # Imputing the data
#   imputed_data[[i]] <- imputing(data_long_missing, data_cleaned_not_imputed, SE_PROP_ED_50_gamma)
#   # Creating a matrix
#   imputed_vcv[[i]]  <- metafor::vcalc(vi = LRR_VAR_INDIVIDUAL,
#                cluster = STUDY_ID,
#                obs = MULTIPLE_TYPE,
#                grp1 = CONTROL_GROUP,
#                grp2 = TEST_GROUP,
#                w1 = AI_N_INDIVIDUAL,
#                w2 = FORM_N_INDIVIDUAL,
#                time1 = TIME_SIMPLE,
#                phi = 0.8,
#                rho = 0.8,
#                data= imputed_data[[i]])
# 
#   # Creating a model
#   imputed_model[[i]] <- rma.mv(yi = LRR, V = imputed_vcv[[i]],
#                               mod = ~ 0 + PESTICIDE_CLASS,
#                               random = list(~1 | STUDY_ID,
#                                             ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
#                               struct = "AR",
#                               data = imputed_data[[i]], method = "REML", test = "t", dfs = "contain")
# 
#   # Get a row
#   row <- estim_mod_wide(imputed_model[[i]], i)
# 
#    imputed_estimates <- bind_rows(imputed_estimates, row)
#  }
# 
# imputed_estimates <- imputed_estimates %>%
#   rename(run = model)

```


```{r}
#write_csv(imputed_estimates, "output/imputation_results_moderator_level.csv")
```

Now that the 100 rounds of imputation have been done, we compare the quantiles with the estimates without imputation, and we will select the median based on herbicide estimate.

```{r}
imputed_estimates <- read_csv("output/imputation_results_moderator_level.csv") 

summary_quantiles <- imputed_estimates %>%
  # Remove the run column to summarize only numeric results
  dplyr::select(-run) %>%
  # Pivot longer so each estimate or CI per pesticide is a row with its variable name
  pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "value"
  ) %>%
  # Group by variable 
  group_by(variable) %>%
  # Compute quantiles per variable
  summarise(
    q05 = quantile(value, probs = 0.05, na.rm = TRUE),
    median = quantile(value, probs = 0.5, na.rm = TRUE),
    q95 = quantile(value, probs = 0.95, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  # Optionally, pivot wider to get rows as quantiles and columns as variables
  pivot_longer(
    cols = c(q05, median, q95),
    names_to = "quantile",
    values_to = "estimate"
  ) %>%
  pivot_wider(
    names_from = variable,
    values_from = estimate
  ) %>%
  # Fix quantile order if needed
  mutate(quantile = factor(quantile, levels = c("q05", "median", "q95"))) %>%
  arrange(quantile) %>%
  rename(model = quantile)

# Changing the orders of columns
# Get pesticide names from column suffixes
pesticides <- sub(".*_(.*)", "\\1", grep("^estimate_", names(summary_quantiles), value = TRUE))

# Build the desired column order
ordered_cols <- c("model", unlist(lapply(pesticides, function(p) {
  c(paste0("estimate_", p), paste0("lower_", p), paste0("upper_", p))
})))

# Reorder columns
quantiles_ordered <- summary_quantiles[, ordered_cols]

# Comparing with the model without imputation

est_final <- estim_mod_wide(final_model_reml, "without imputation")

comparison <- bind_rows(quantiles_ordered, est_final)  


# Format for output
# Create the HTML table with grouped headers
final_table_comp <- comparison %>%
  mutate(across(-model, ~ round(.x, 4))) %>%
  knitr::kable("html",
               digits = 4,
               col.names = c("Model",
                             rep(c("Estimate", "Lower CI", "Upper CI"), 3))) %>%
  add_header_above(c(" " = 1,
                     "Fungicide" = 3,
                     "Herbicide" = 3,
                     "Insecticide" = 3)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))


#  Save
save_kable(final_table_comp, "output/effect_of_imputation_se_draws.pdf")
```

```{r}
# # This code chunk will not work if the 100 imputations have not been done, so it's commented and the data is saved
# # what is the median model in terms of herbicide LRR estimate?
# # Order the estimates according to herbicide estimate
# median_herbicide_run <- imputed_estimates %>%
#   arrange(estimate_herbicide) %>%
#   slice(50)%>%
#   pull(run)
# 
# data_cleaned_imputed_gamma <- imputed_data[[median_herbicide_run]]
# 
# write_csv(data_cleaned_imputed, "output/results_imputation.csv")
```

```{r}
data_cleaned_imputed_gamma <- read_csv("output/results_imputation.csv")%>%
  mutate(AI_NAME = str_to_lower(AI_NAME))

matrix_gamma <- metafor::vcalc(vi = LRR_VAR_INDIVIDUAL,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_N_INDIVIDUAL,
               w2 = FORM_N_INDIVIDUAL,
               time1 = TIME_SIMPLE,
               phi = 0.8,
               rho = 0.8,
               data= data_cleaned_imputed_gamma)

model_gamma <- rma.mv(yi = LRR, V = matrix_gamma,
                                mod = ~ 0 + PESTICIDE_CLASS,
                                random = list(~1 | STUDY_ID,
                                              ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                                struct = "AR",
                                data = data_cleaned_imputed_gamma, method = "REML", test = "t", dfs = "contain")


data_cleaned_imputed_gamma_wt_phylo <- data_cleaned_imputed_gamma %>%
  filter(!REASON_EXCLUSION %in% c("microbial_or_cells","Name_not_in_open_tree"))
```
### Second method

This is based on Nagawaka et al 2023, "A robust and readily implementable method for the metaanalysis of response ratios with and without missing standard deviations". I will test several of their proposed methods, and I'm using code from their tutorial. 

#### Missing cases method 

```{r}
# Creating the SD columns 
data_cleaned_imputed_1 <- data_cleaned_not_imputed %>%
  mutate(AI_SD_INDIVIDUAL = AI_SE_INDIVIDUAL*sqrt(AI_N_INDIVIDUAL),
         FORM_SD_INDIVIDUAL = FORM_SE_INDIVIDUAL*sqrt(FORM_N_INDIVIDUAL)) %>%
# And the CV columns 
  mutate(CV_AI = na_if(AI_SD_INDIVIDUAL/AI_50, Inf),
         CV_FORM = na_if(FORM_SD_INDIVIDUAL/FORM_50, Inf))

# Using a function from Nagawaka et al to build the coefficient of variation (CV)
data_cleaned_imputed_1 <- cv_avg(x = AI_50, sd = AI_SD_INDIVIDUAL,
                            n = AI_N_INDIVIDUAL, group = STUDY_ID, label = "AI",
                             data = data_cleaned_imputed_1)

data_cleaned_imputed_1 <- cv_avg(x = FORM_50, sd = FORM_SD_INDIVIDUAL,
                            n = FORM_N_INDIVIDUAL, group = STUDY_ID,
                            label = "FORM", data = data_cleaned_imputed_1)

 # Use weighted mean CV in replacement for where CV's are missing. Otherwise, calculate CV^2 of data that is known.
data_cleaned_imputed_1 <- data_cleaned_imputed_1 %>%
   mutate(CV2_AI = if_else(is.na(CV_AI),      b_CV2_AI, CV_AI^2),
          CV2_FORM = if_else(is.na(CV_FORM), b_CV2_FORM, CV_FORM^2)) %>%
# Compute variance
   mutate(LRR_VAR_N0 = v_lnrr_laj(cv1 = CV2_AI, n1= AI_N_INDIVIDUAL,
                                  cv2 = CV2_FORM, n2 = FORM_N_INDIVIDUAL))


matrix0 <- metafor::vcalc(vi = LRR_VAR_N0,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_N_INDIVIDUAL,
               w2 = FORM_N_INDIVIDUAL,
               time1 = TIME_SIMPLE,
               phi = 0.8,
               rho = 0.8,
               data= data_cleaned_imputed_1)

model0 <- rma.mv(yi = LRR, V = matrix0,
                                mod = ~ 0 + PESTICIDE_CLASS,
                                random = list(~1 | STUDY_ID,
                                              ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                                struct = "AR",
                                data = data_cleaned_imputed_1, method = "REML", test = "t", dfs = "contain")



```


#### All cases methods

Now,  using the all-cases method, that they recommend as the best in their paper. They use SD as the measurement of error, but we use the sample size to go from SE to SD. 

```{r}
# In this case, we build the variance using CV for all rows 
data_cleaned_imputed_1 <- data_cleaned_imputed_1 %>%
  mutate(LRR_VAR_N1 = v_lnrr_laj(cv1 = b_CV2_AI, n1= AI_N_INDIVIDUAL,
                                 cv2 = b_CV2_FORM, n2 = FORM_N_INDIVIDUAL))

matrix1 <- metafor::vcalc(vi = LRR_VAR_N1,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_N_INDIVIDUAL,
               w2 = FORM_N_INDIVIDUAL,
               time1 = TIME_SIMPLE,
               phi = 0.8,
               rho = 0.8,
               data= data_cleaned_imputed_1)

model1 <- rma.mv(yi = LRR, V = matrix1,
                                mod = ~ 0 + PESTICIDE_CLASS,
                                random = list(~1 | STUDY_ID,
                                              ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                                struct = "AR",
                                data = data_cleaned_imputed_1, method = "REML", test = "t", dfs = "contain")


```

#### Hybrid method

Here testing the hybrid method, as the visualisations showed that in my dataset, missing SE/SD are not random but associated with bigger TDDs. However, not sure how their code can have an influence on that. 

```{r}
# Hybrid method  
missing_dat <- which(is.na(data_cleaned_imputed_1$AI_SD_INDIVIDUAL) | is.na(data_cleaned_imputed_1$FORM_SD_INDIVIDUAL))

# Set the effect sizes not missing data to zero in the V_es matrix
V_es2 <- diag(data_cleaned_imputed_1$LRR_VAR_N1)
diag(V_es2)[-missing_dat] <- 0
row.names(V_es2) <- data_cleaned_imputed_1$DATA_ID
data_cleaned_imputed_1$obs2 <- rownames(V_es2)

# Set the v_lnrr_laj to 0
data_cleaned_imputed_1$LRR_VAR_N2 <- data_cleaned_imputed_1$LRR_VAR_N1
data_cleaned_imputed_1$LRR_VAR_N2[missing_dat] <- 0
    
matrix2 <- metafor::vcalc(vi = LRR_VAR_N2,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_N_INDIVIDUAL,
               w2 = FORM_N_INDIVIDUAL,
               time1 = TIME_SIMPLE,
               phi = 0.8,
               rho = 0.8,
               data= data_cleaned_imputed_1)


    
model2 <- rma.mv(yi = LRR, V = matrix2,
                                mod = ~ 0 + PESTICIDE_CLASS,
                                random = list(~1 | STUDY_ID,
                                              ~ 1 | obs2,
                                              ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                                struct = "AR",
                                data = data_cleaned_imputed_1,
                                 R = list(obs2=V_es2),
                                 method = "REML", test = "t", dfs = "contain", Rscale=F)
    

```
### Comparison of methods 

```{r, warning=FALSE}
# Getting estimates 
est_impg <- estim_mod_wide(model_gamma, "Gamma imputation")
est_imp0 <- estim_mod_wide(model0, "Missing cases method")
est_imp1 <- estim_mod_wide(model1, "All-cases method")
est_imp2 <- estim_mod_wide(model2, "Hybrid method ")

comparison_all <- bind_rows(est_final, est_impg, est_imp0, est_imp1, est_imp2)

# Saving a table 

final_table_all <- comparison_all %>%
  knitr::kable("html",
               digits = 4,
               col.names = c("Model",
                             rep(c("Estimate", "Lower CI", "Upper CI"), 3))) %>%
  add_header_above(c(" " = 1,
                     "Fungicide" = 3,
                     "Herbicide" = 3,
                     "Insecticide" = 3)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))



save_kable(final_table_all, "output/Different_imputation_methods_table.pdf")

# Saving plots 

imputed_model_plot <- orchard_plot(model_gamma, 
                                         mod = "PESTICIDE_CLASS", 
                                         xlab = "Effect size lnRR", 
                                         group = "STUDY_ID",  k = TRUE, g = TRUE, trunk.size = 1.5) +
  scale_fill_manual(values = c("#CC79A7","#009E73", "#F0E442") ) +
  scale_colour_manual(values = c("#CC79A7","#009E73", "#F0E442"))+
  ggtitle("Imputation Gamma Method ")

imputed_model_plot0 <- orchard_plot(model0, 
                                         mod = "PESTICIDE_CLASS", 
                                         xlab = "Effect size lnRR", 
                                         group = "STUDY_ID",  k = TRUE, g = TRUE, trunk.size = 1.5) +
  scale_fill_manual(values = c("#CC79A7","#009E73", "#F0E442") ) +
  scale_colour_manual(values = c("#CC79A7","#009E73", "#F0E442"))+
  ggtitle("Missing Cases Method ")


imputed_model_plot1 <- orchard_plot(model1, 
                                         mod = "PESTICIDE_CLASS", 
                                         xlab = "Effect size lnRR", 
                                         group = "STUDY_ID",  k = TRUE, g = TRUE, trunk.size = 1.5) +
  scale_fill_manual(values = c("#CC79A7","#009E73", "#F0E442") ) +
  scale_colour_manual(values = c("#CC79A7","#009E73", "#F0E442"))+
  ggtitle("Imputation All Cases Method ")



imputed_model_plot2 <- orchard_plot(model2, 
                                         mod = "PESTICIDE_CLASS", 
                                         xlab = "Effect size lnRR", 
                                         group = "STUDY_ID",  k = TRUE, g = TRUE, trunk.size = 1.5) +
  scale_fill_manual(values = c("#CC79A7","#009E73", "#F0E442") ) +
  scale_colour_manual(values = c("#CC79A7","#009E73", "#F0E442"))+
  ggtitle("Imputation Hybrid Method ")


# Open the PDF
cairo_pdf("output/Different_imputation_methods_Plots.pdf", width = 10, height = 12)

# Print plots with titles
final_model_plot / (imputed_model_plot0 + imputed_model_plot) / (imputed_model_plot1 + imputed_model_plot2)  # stacked vertically

# Close the device
dev.off()

```

From this analysis, I decided to keep the imputed data from the missing case methods

```{r}
# Changing the references to the missing cases method
data_cleaned_imputed <- data_cleaned_imputed_1 %>%
  dplyr::select(-LRR_VAR_INDIVIDUAL) %>%
  rename(LRR_VAR_INDIVIDUAL = LRR_VAR_N0)



autocorrelation_matrix <- metafor::vcalc(vi = LRR_VAR_INDIVIDUAL,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_N_INDIVIDUAL,
               w2 = FORM_N_INDIVIDUAL,
               time1 = TIME_SIMPLE,
               phi = 0.8,
               rho = 0.8,
               data= data_cleaned_imputed)

final_model_imputed <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                                mod = ~ 0 + PESTICIDE_CLASS,
                                random = list(~1 | STUDY_ID,
                                              ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                                struct = "AR",
                                data = data_cleaned_imputed, method = "REML", test = "t", dfs = "contain")

final_est_imputed <- estim_mod_wide(final_model_imputed, "Final imputed ")

final_imputed_plot <- orchard_plot(final_model_imputed, 
                                         mod = "PESTICIDE_CLASS", 
                                         xlab = "Effect size lnRR", 
                                         group = "STUDY_ID",  k = TRUE, g = TRUE, trunk.size = 1.5) +
  scale_fill_manual(values = c("violetred3","yellowgreen", "goldenrod1") ) +
  scale_colour_manual(values = c("violetred3","yellowgreen", "goldenrod1"))

final_imputed_plot
```


## Leave one out analysis 

Here I  run a leave 1 out analysis to determine if some effect sizes have a too big impact on the results. If one row is responsible for the significance of a moderator, it will be excluded. The chunk below takes a long, long time (2h) to run, so the results have been save in the output and the chunk is commented. 

In my dataset, it resulted in 5 rows being excluded. They are excluded earlier in the markdown, but this is here because it comes after the model selection. Here I show the saved results that motived the exclusions. If you want to re-do the analysis yourslelf, you need to comment the exclusions earlier and decomment here.

This was run with the imputation from the missing case case method. 

```{r}

# # Helper function for one iteration
# # the dataset to use is hardcoded in the function, which is not good practice, but I think it's need to be if I want to use map_dfr after ? 
# fit_leave1out_model <- function(data_id_to_drop) {
# 
#   dat <- data_cleaned_imputed %>% filter(DATA_ID != data_id_to_drop)
# 
#   vcv <- metafor::vcalc(vi = LRR_VAR_INDIVIDUAL,
#                cluster = STUDY_ID,
#                obs = MULTIPLE_TYPE,
#                grp1 = CONTROL_GROUP,
#                grp2 = TEST_GROUP,
#                w1 = AI_N_INDIVIDUAL,
#                w2 = FORM_N_INDIVIDUAL,
#                time1 = TIME_SIMPLE,
#                phi = 0.8,
#                rho = 0.8,
#                data= dat)
# 
#  mod <- rma.mv(yi = LRR, V = vcv,
#                mod = ~ 0 + PESTICIDE_CLASS,
#               random = list(~1 | STUDY_ID,
#                              ~TIME_SIMPLE | MULTIPLE_MEASUREMENT),
#                struct = "AR",
#                data = dat, method = "REML", test = "t", dfs = "contain")
# 
#   # Extract coefficients in wide format
#   df <- estim_mod_wide(mod, data_id_to_drop) %>%
#     rename(DATA_ID = model)
# 
#   return(df)
# }
# 
# 
# 
# # Run leave-one-out over all DATA_IDs
# leave1out_results <- map_dfr(data_cleaned_imputed$DATA_ID, fit_leave1out_model)

```

```{r}
# write_csv(leave1out_results, "Output/leave1out_results_missingcase.csv")
```

Now we search for rows that affect the significance of the results. 

```{r}
leave1out_results <- read_csv("Output/leave1out_results_missingcase.csv")

# Putting it in a long format 
est_final_long <- final_est_imputed %>%
  pivot_longer(
    cols = -model,
    names_to = c("type", "class"),
    names_pattern = "(estimate|lower|upper)_(.*)"
  ) %>%
  pivot_wider(names_from = type, values_from = value) %>%
  rename(id = model)

loo_estimates_long <- leave1out_results %>%
  pivot_longer(
    cols = -DATA_ID,
    names_to = c("type", "class"),
    names_pattern = "(estimate|lower|upper)_(.*)"
  ) %>%
  pivot_wider(names_from = type, values_from = value)

# Making the comparison
# Comparing the signs of estimates and of both CI 
check_leave1out <-  loo_estimates_long %>%
  left_join(est_final_long, by = "class", suffix = c("_loo", "_final")) %>%
  mutate(
    sign_change = sign(estimate_loo) != sign(estimate_final),
    sig_loo = !(lower_loo < 0 & upper_loo > 0),
    sig_final = !(lower_final < 0 & upper_final > 0),
    significance_change = sig_loo != sig_final
  )

comparison_loo <- check_leave1out %>%
  group_by(class) %>%
  summarise(
    sign_changes = sum(sign_change),
    sig_changes = sum(significance_change),
    total = n(),
  )


which_loo <- check_leave1out %>%
  filter( significance_change == TRUE | sign_change == TRUE)


influential <- data_cleaned_imputed %>%
  filter(DATA_ID %in% which_loo$DATA_ID)

```

Since this analysis identify one row that can change the significance of the fungicide results, I'm gonna exclude it and re-run the analysis, to see if results are stable now 

```{r}
# data_cleaned_imputed <- data_cleaned_imputed %>%
#   filter(!DATA_ID %in% which_loo$DATA_ID)
# 
# # Red-do the leave-1-out analyis  
# 
# leave1out_results_bis <- map_dfr(data_cleaned_imputed$DATA_ID, fit_leave1out_model)
```

```{r}
# write_csv(leave1out_results_bis, "Output/leave1out_results_missingcase_bis.csv")
```

```{r}
leave1out_results_bis <- read_csv("Output/leave1out_results_missingcase_bis.csv")

# Putting it in a long format 

loo_estimates_long_bis <- leave1out_results_bis %>%
  pivot_longer(
    cols = -DATA_ID,
    names_to = c("type", "class"),
    names_pattern = "(estimate|lower|upper)_(.*)"
  ) %>%
  pivot_wider(names_from = type, values_from = value)

# Making the comparison
# Comparing the signs of estimates and of both CI 
check_leave1out_bis <-  loo_estimates_long_bis %>%
  left_join(est_final_long, by = "class", suffix = c("_loo", "_final")) %>%
  mutate(
    sign_change = sign(estimate_loo) != sign(estimate_final),
    sig_loo = !(lower_loo < 0 & upper_loo > 0),
    sig_final = !(lower_final < 0 & upper_final > 0),
    significance_change = sig_loo != sig_final
  )

comparison_loo_bis <- check_leave1out_bis %>%
  group_by(class) %>%
  summarise(
    sign_changes = sum(sign_change),
    sig_changes = sum(significance_change),
    total = n(),
  )


which_loo_bis <- check_leave1out_bis %>%
  filter( significance_change == TRUE | sign_change == TRUE)


influential_bis <- data_cleaned_imputed_influential %>%
  filter(DATA_ID %in% which_loo_bis$DATA_ID)

```

So now what is happening is that almost all rows are considered influential in term of fungicides. I think the fungicides result is not robust anyway. But now I'm gonna exclude the ones not considered influential, because it means that there are the one that change the significance. 

```{r}
influential_real_bis <- data_cleaned_imputed_influential %>%
  filter(!DATA_ID %in% which_loo_bis$DATA_ID) %>%
  filter(PESTICIDE_CLASS == "fungicide") # Because it's only the significance of fungicide affected
```


```{r}
# data_cleaned_imputed <- data_cleaned_imputed %>%
#   filter(!DATA_ID %in% influential_real_bis$DATA_ID)
# 
# # Red-do the leave-1-out analyis  
# 
# leave1out_results_ter <- map_dfr(data_cleaned_imputed$DATA_ID, fit_leave1out_model)
```
```{r}
write_csv(leave1out_results_ter, "output/leave1out_results_missingcase_ter.csv")
```


```{r}
#leave1out_results_ter <- read_csv("Output/leave1out_results_missingcase_ter.csv")

# Putting it in a long format 

loo_estimates_long_ter <- leave1out_results_ter %>%
  pivot_longer(
    cols = -DATA_ID,
    names_to = c("type", "class"),
    names_pattern = "(estimate|lower|upper)_(.*)"
  ) %>%
  pivot_wider(names_from = type, values_from = value)

# Making the comparison
# Comparing the signs of estimates and of both CI 
check_leave1out_ter <-  loo_estimates_long_ter %>%
  left_join(est_final_long, by = "class", suffix = c("_loo", "_final")) %>%
  mutate(
    sign_change = sign(estimate_loo) != sign(estimate_final),
    sig_loo = !(lower_loo < 0 & upper_loo > 0),
    sig_final = !(lower_final < 0 & upper_final > 0),
    significance_change = sig_loo != sig_final
  )

comparison_loo_ter <- check_leave1out_ter %>%
  group_by(class) %>%
  summarise(
    sign_changes = sum(sign_change),
    sig_changes = sum(significance_change),
    total = n(),
  )


which_loo_ter <- check_leave1out_ter %>%
  filter( significance_change == TRUE | sign_change == TRUE)


influential_ter <- data_cleaned_imputed_influential %>%
  filter(DATA_ID %in% which_loo_ter$DATA_ID)
```

The results of this part have been incoporated earlier. 

```{r}
influential_to_exclude <- bind_rows(influential, influential_real_bis)

write_csv(influential_to_exclude, "output/leave1out_to_exclude.csv")
```


## Final models check

### Heterogenity 

We look at the measures of heterogenity in our model. We need to use a simplified model as orchard doesn't take models with heterogenous variance

```{r}
# We fit a simpler model 
final_model_simple_intercept <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ 0 + PESTICIDE_CLASS,
                    random = list(~1 | STUDY_ID/MULTIPLE_MEASUREMENT),
                    data = data_cleaned_imputed, method = "REML", test = "t", dfs = "contain")

final_model_intercept <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                    mod = ~ 1,
                    random = list(~1 | STUDY_ID/MULTIPLE_MEASUREMENT),
                    data = data_cleaned_imputed, method = "REML", test = "t", dfs = "contain")



# Using the orchard package
i2_ml(final_model_simple_intercept)
r2_ml(final_model_simple_intercept)



```
R2 marginal indicates that PESTICIDE_CLASS can explain 29.5 % of the variation. Now we try to manually obtain I2 estimates for the not simplified model 
```{r}
# adapted from source linked above
W <- solve(autocorrelation_matrix)
X <- model.matrix(final_model_imputed)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W

# I^2 total
I2_t <-  100 * sum(final_model_imputed$sigma2,final_model_imputed$tau2) / (sum(final_model_imputed$sigma2,final_model_imputed$tau2) + (final_model_imputed$k-final_model_imputed$p)/sum(diag(P)))

# between study
I2_betweenstudy <- 100 * final_model_imputed$sigma2/ (sum(final_model_imputed$sigma2,final_model_imputed$tau2) + (final_model_imputed$k-final_model_imputed$p)/sum(diag(P)))

# within study
I2_withinwtudy <- 100 * final_model_imputed$tau2/ (sum(final_model_imputed$sigma2,final_model_imputed$tau2) + (final_model_imputed$k-final_model_imputed$p)/sum(diag(P)))

# sampling variance
Sampling_variance <- 100 - (100 * sum(final_model_imputed$sigma2,final_model_imputed$tau2) / (sum(final_model_imputed$sigma2,final_model_imputed$tau2) + (final_model_imputed$k-final_model_imputed$p)/sum(diag(P))))

I2_t
I2_betweenstudy
I2_withinwtudy
Sampling_variance

# Tau
# To see the variance components (tau) for each random effect:
summary(final_model_imputed)
predict(final_model_intercept)
```


### Profile plots 

Makes sure that the likelihood surface around the ML/REML estimates is not flat for some combination of the parameter estimates (which would imply that the estimates are essentially arbitrary). Seems to be fine.

This also takes a long time to run, so it has been commented 

```{r}
# profile(final_model_reml,
#        progbar=TRUE,
#        parallel="multicore")
# 
# par(mfrow=c(3,1))
# 
# profile.rma.mv(final_model_reml,
#               tau2 = 1)
# 
# profile.rma.mv(final_model_reml,
#                sigma2 = 1)
# 
# profile(final_model_reml, rho=1, xlim=c(0.90, 1))
# 
# 
# cairo_pdf("output/parameter_identifiability_0.pdf")
# profile(final_model_reml,
#        progbar=TRUE,
#        parallel="multicore")
# dev.off()
# 
# cairo_pdf("output/parameter_identifiability.pdf")
# par(mfrow=c(3,1))
# 
# profile.rma.mv(final_model_reml,
#                tau2 = 1)
# 
# profile.rma.mv(final_model_reml,
#                sigma2 = 1)
# 
# profile(final_model_reml, rho=1, xlim=c(0.90, 1))
# dev.off()
```


```{r}
# profile(final_model_imputed,
#        progbar=TRUE,
#        parallel="multicore")
# 
# par(mfrow=c(3,1))
# 
# profile.rma.mv(final_model_imputed,
#               tau2 = 1)
# 
# profile.rma.mv(final_model_imputed,
#                sigma2 = 1)
# 
# profile(final_model_imputed, rho=1, xlim=c(0.90, 1))
# 
# 
# cairo_pdf("output/parameter_identifiability_0_imputed.pdf")
# profile(final_model_imputed,
#        progbar=TRUE,
#        parallel="multicore")
# dev.off()
# 
# cairo_pdf("output/parameter_identifiability_imputed.pdf")
# par(mfrow=c(3,1))
# 
# profile.rma.mv(final_model_imputed,
#                tau2 = 1)
# 
# profile.rma.mv(final_model_imputed,
#                sigma2 = 1)
# 
# profile(final_model_imputed, rho=1, xlim=c(0.90, 1))
# dev.off()
```


## Sensitivity Analysis 

```{r}
# Define a function that fits a model and estimates 
fit_mod <- function(data){
  matrix <- metafor::vcalc(vi = LRR_VAR_INDIVIDUAL,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_N_INDIVIDUAL,
               w2 = FORM_N_INDIVIDUAL,
               time1 = TIME_SIMPLE,
               phi = 0.8,
               rho = 0.8,
               data= data)

  model <- rma.mv(yi = LRR, V = matrix,
                                mod = ~ 0 + PESTICIDE_CLASS,
                                random = list(~1 | STUDY_ID,
                                              ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                                struct = "AR",
                                data = data, method = "REML", test = "t", dfs = "contain")

  
  return(model)
}
```

### Publication Bias 


First, let's look at some funnel plots
```{r, warning=FALSE}
data_cleaned_imputed <- data_cleaned_imputed %>%
  mutate(LRR_SE = sqrt(LRR_VAR_INDIVIDUAL)) %>%
  mutate(PRECISION = 1/LRR_SE) %>%
  mutate(YEAR_CEN = scale(YEAR_PUBLISHED, scale = FALSE) %>% as.vector())

ggplot(data_cleaned_imputed, aes(x = LRR, y = PRECISION))+
  geom_point(alpha = 0.5, colour = "black")+ 
  #ylim(c(0,10))+
  xlim(c(-8,8))+
  theme_bw()

funnel(data_cleaned_imputed$LRR, data_cleaned_imputed$LRR_VAR_INDIVIDUAL, yaxis="seinv",
       #xlim = c(-3, 3),
       ylab = "Precision (1/SE)",
       xlab = "Effect size (lnRR)")




# Just for herbicides
ggplot(data_cleaned_imputed %>%
         filter(PESTICIDE_CLASS == "herbicide"), aes(x = LRR, y = PRECISION, colour = SE_SIMULATION_REQUIRED))+
  geom_point(alpha = 0.5)+ 
  theme_bw()


```
Now we test formally for publication bias by incorporating it in the predictors. 

```{r}
# All in model
publication_bias_all_mod <- rma.mv(yi = LRR, V = autocorrelation_matrix,
                                                mods= ~ 1 + LRR_SE + YEAR_CEN + PESTICIDE_CLASS,
                                                random = list(~1 | STUDY_ID,
                                                              ~ 1 | DATA_ID,
                                                              ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                                                struct = "AR",
                                                data = data_cleaned_imputed, method = "REML", test = "t", dfs = "contain")

summary(publication_bias_all_mod)
```
The all-in model does not detect publication bias, whether it is decline effect or small study effect. 
Now we use the model to predict and plot. 

```{r}
# This chunk is a bit lengthy because for each pesticide, we create an empty tibble, populate it, predict and then plot
# create a grid of new moderator value
X_names <- colnames(model.matrix(~ LRR_SE + YEAR_CEN + PESTICIDE_CLASS, data = data_cleaned_imputed))

# Create a tibble with zeros, except for the sequence for SQRT_INV_N_TILDA and the correct class set to 1
# Herbicide
pred_data_herb <- tibble(
  LRR_SE = seq(
    min(data_cleaned_imputed$LRR_SE),
    max(data_cleaned_imputed$LRR_SE),
    length.out = nrow(data_cleaned_imputed)
  )
) %>%
  mutate(across(everything(), ~ .x)) %>%                      # keep the first column
  bind_cols(as_tibble(matrix(0, nrow(.), length(X_names) - 2))) %>%  # add the other columns as 0s
  setNames(X_names[-1])                                            # apply column names from model.matrix

pred_data_herb$`PESTICIDE_CLASSherbicide` <- 1
# predict
pb_all_pred_herb <- predict(publication_bias_all_mod,
                                                newmods=as.matrix(pred_data_herb))



pred_se_herb <- data.frame(sint = seq(min(data_cleaned_imputed$LRR_SE),
                                                      max(data_cleaned_imputed$LRR_SE),
                                                      length.out=nrow(data_cleaned_imputed)),
                                           PESTICIDE_CLASS = "herbicide",
                                           fit = pb_all_pred_herb$pred,
                                           upper = pb_all_pred_herb$ci.ub,
                                           lower = pb_all_pred_herb$ci.lb)

# Insecticide
pred_data_ins <- tibble(
  LRR_SE = seq(
    min(data_cleaned_imputed$LRR_SE),
    max(data_cleaned_imputed$LRR_SE),
    length.out = nrow(data_cleaned_imputed)
  )
) %>%
  mutate(across(everything(), ~ .x)) %>%                      # keep the first column
  bind_cols(as_tibble(matrix(0, nrow(.), length(X_names) - 2))) %>%  # add the other columns as 0s
  setNames(X_names[-1])                                            # apply column names from model.matrix

pred_data_ins$`PESTICIDE_CLASSinsecticide` <- 1
# predict
pb_all_pred_ins <- predict(publication_bias_all_mod,
                                                newmods=as.matrix(pred_data_ins))



pred_se_ins <- data.frame(sint = seq(min(data_cleaned_imputed$LRR_SE),
                                                      max(data_cleaned_imputed$LRR_SE),
                                                      length.out=nrow(data_cleaned_imputed)),
                                           PESTICIDE_CLASS = "insecticide",
                                           fit = pb_all_pred_ins$pred,
                                           upper = pb_all_pred_ins$ci.ub,
                                           lower = pb_all_pred_ins$ci.lb)

# Plotting 
pred_se_plot <- ggplot() +
  # Points
  geom_point(data = data_cleaned_imputed,
             aes(x = LRR_SE,                                  
                 y = LRR,
                 group = PESTICIDE_CLASS,
                 color = PESTICIDE_CLASS), 
             alpha = 0.5) +
  # Trend for herbicide
  geom_line(data = pred_se_herb,
             aes(x = sint,
                 y = fit,
                 group = PESTICIDE_CLASS,
                 color = PESTICIDE_CLASS)) +
  geom_ribbon(data = pred_se_herb,
              aes(x = sint,
                  y = fit,
                  ymin = lower,
                  ymax = upper,
                  group = PESTICIDE_CLASS,
                  color = PESTICIDE_CLASS,
                  fill = PESTICIDE_CLASS),
              alpha = 0.3) +
  # Trend for insecticide
  geom_line(data = pred_se_ins,
             aes(x = sint,
                 y = fit,
                 group = PESTICIDE_CLASS,
                 color = PESTICIDE_CLASS)) +
  geom_ribbon(data = pred_se_ins,
              aes(x = sint,
                  y = fit,
                  ymin = lower,
                  ymax = upper,
                  group = PESTICIDE_CLASS,
                  color = PESTICIDE_CLASS,
                  fill = PESTICIDE_CLASS),
              alpha = 0.3) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  scale_color_manual(values = c("#CC79A7",
                                "#009E73",
                                "#F0E442" ),
                     name = "Pesticide Class",
                     labels = c( "Fungicide","Herbicide", "Insecticide")) +
  scale_fill_manual(values = c("grey60", "grey60"),
                    name = "", labels = c("")) +
  xlab("Standard error") +
  ylab("Effect size (lnRR)") +
  #ggtitle("Small Study effect") +
  guides(color=guide_legend(override.aes=list(fill=NA, linetype=0)),
                                            fill = "none")

pred_se_plot

cairo_pdf("output/small_study_effect.pdf")
pred_se_plot
dev.off()
```

```{r}
# Decline effect, predict for a range of years

# Create a grid of new moderator value based on YEAR_CEN instead of LRR_SE
X_names <- colnames(model.matrix(~ LRR_SE + YEAR_CEN + PESTICIDE_CLASS, data = data_cleaned_imputed))

# HERBICIDE predictions
pred_data_herb <- tibble(
  YEAR_CEN = seq(
    min(data_cleaned_imputed$YEAR_CEN),
    max(data_cleaned_imputed$YEAR_CEN),
    length.out = nrow(data_cleaned_imputed)
  )
) %>%
  mutate(across(everything(), ~ .x)) %>%
  bind_cols(as_tibble(matrix(0, nrow(.), length(X_names) - 2))) %>%
  setNames(X_names[-1])

pred_data_herb$`PESTICIDE_CLASSherbicide` <- 1

pb_all_pred_herb <- predict(publication_bias_all_mod,
                            newmods = as.matrix(pred_data_herb))

pred_year_herb <- data.frame(
  sint = seq(min(data_cleaned_imputed$YEAR_PUBLISHED),
             max(data_cleaned_imputed$YEAR_PUBLISHED),
             length.out = nrow(data_cleaned_imputed)),
  PESTICIDE_CLASS = "herbicide",
  fit = pb_all_pred_herb$pred,
  upper = pb_all_pred_herb$ci.ub,
  lower = pb_all_pred_herb$ci.lb
)

# INSECTICIDE predictions
pred_data_ins <- tibble(
  YEAR_CEN = seq(
    min(data_cleaned_imputed$YEAR_CEN),
    max(data_cleaned_imputed$YEAR_CEN),
    length.out = nrow(data_cleaned_imputed)
  )
) %>%
  mutate(across(everything(), ~ .x)) %>%
  bind_cols(as_tibble(matrix(0, nrow(.), length(X_names) - 2))) %>%
  setNames(X_names[-1])

pred_data_ins$`PESTICIDE_CLASSinsecticide` <- 1

pb_all_pred_ins <- predict(publication_bias_all_mod,
                           newmods = as.matrix(pred_data_ins))

pred_year_ins <- data.frame(
  sint = seq(min(data_cleaned_imputed$YEAR_PUBLISHED),
             max(data_cleaned_imputed$YEAR_PUBLISHED),
             length.out = nrow(data_cleaned_imputed)),
  PESTICIDE_CLASS = "insecticide",
  fit = pb_all_pred_ins$pred,
  upper = pb_all_pred_ins$ci.ub,
  lower = pb_all_pred_ins$ci.lb
)

# PLOT
pred_year_plot <- ggplot() +
  geom_point(data = data_cleaned_imputed,
             aes(x = YEAR_PUBLISHED,
                 y = LRR,
                 group = PESTICIDE_CLASS,
                 color = PESTICIDE_CLASS), 
             alpha = 0.5) +
  geom_line(data = pred_year_herb,
            aes(x = sint, y = fit, group = PESTICIDE_CLASS, color = PESTICIDE_CLASS)) +
  geom_ribbon(data = pred_year_herb,
              aes(x = sint, y = fit, ymin = lower, ymax = upper,
                  group = PESTICIDE_CLASS, fill = PESTICIDE_CLASS, color = PESTICIDE_CLASS),
              alpha = 0.3) +
  geom_line(data = pred_year_ins,
            aes(x = sint, y = fit, group = PESTICIDE_CLASS, color = PESTICIDE_CLASS)) +
  geom_ribbon(data = pred_year_ins,
              aes(x = sint, y = fit, ymin = lower, ymax = upper,
                  group = PESTICIDE_CLASS, fill = PESTICIDE_CLASS, color = PESTICIDE_CLASS),
              alpha = 0.3) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  scale_color_manual(values = c("#CC79A7", "#009E73", "#F0E442"),
                     name = "Pesticide Class",
                     labels = c("Fungicide", "Herbicide", "Insecticide")) +
  scale_fill_manual(values = c("grey60", "grey60"),
                    name = "", labels = c("")) +
  xlab("Publication Year") +
  ylab("Effect size (lnRR)") +
  guides(color = guide_legend(override.aes = list(fill = NA, linetype = 0)),
         fill = "none")

pred_year_plot

cairo_pdf("output/decline_effect.pdf")
pred_year_plot
dev.off()

```
### Regulatory guidelines

```{r}
# Fitting the models and computing estimates 
guidelines_followed <- data_cleaned_imputed %>%
  filter(REGULATORY_STANDARDISED_GUIDELINES_FOLLOWED == "YES")

no_guidelines_followed <- data_cleaned_imputed %>%
  filter(REGULATORY_STANDARDISED_GUIDELINES_FOLLOWED == "NO")

guidelines_mod <- fit_mod(guidelines_followed)

est_gdl <- estim_mod_wide(guidelines_mod, "Guidelines followed")

no_guidelines_mod <- fit_mod(no_guidelines_followed)

est_no_gdl <- estim_mod_wide(no_guidelines_mod, "No guidelines followed")


# Creating a table

comp_gdl <- bind_rows(est_gdl, est_no_gdl, final_est_imputed)

table_gdl <- comp_gdl %>%
  knitr::kable("html",
               digits = 4,
               col.names = c("Model",
                             rep(c("Estimate", "Lower CI", "Upper CI"), 3))) %>%
  add_header_above(c(" " = 1,
                     "Fungicide" = 3,
                     "Herbicide" = 3,
                     "Insecticide" = 3)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))



save_kable(table_gdl, "output/guidelines_comparison.pdf")

# Creating a plot 

gdl_plot <- orchard_plot(guidelines_mod, 
                                         mod = "PESTICIDE_CLASS", 
                                         xlab = "Effect size lnRR", 
                                         group = "STUDY_ID",  k = TRUE, g = TRUE, trunk.size = 1.5) +
  scale_fill_manual(values = c("#CC79A7", "#009E73", "#F0E442")) +
  scale_colour_manual(values = c("#CC79A7", "#009E73", "#F0E442"))+
  ggtitle("Guidelines followed")


no_gdl_plot <- orchard_plot(no_guidelines_mod, 
                                         mod = "PESTICIDE_CLASS", 
                                         xlab = "Effect size lnRR", 
                                         group = "STUDY_ID",  k = TRUE, g = TRUE, trunk.size = 1.5) +
  scale_fill_manual(values = c("#CC79A7", "#009E73", "#F0E442")) +
  scale_colour_manual(values = c("#CC79A7", "#009E73", "#F0E442"))+
  ggtitle("No Guidelines followed")


cairo_pdf("output/guidelines_comparison_orchard_plot.pdf", width = 8, height = 13)
gdl_plot / no_gdl_plot / final_imputed_plot
dev.off() 
```
### Animals 
```{r}
# Filtering 
data_cleaned_imputed_animals <- data_cleaned_imputed %>%
  filter(SPECIES_KINGDOM == "Animalia")

data_cleaned_imputed_not_animals <- data_cleaned_imputed %>%
  filter(!SPECIES_KINGDOM == "Animalia")

mod_animals <- fit_mod(data_cleaned_imputed_animals)

est_animals <- estim_mod_wide(mod_animals, "Animals")

mod_other <- fit_mod(data_cleaned_imputed_not_animals)

est_other <- estim_mod_wide(mod_other, "Other")


comp_animals <- bind_rows(est_animals, est_other, final_est_imputed)

table_animals <- comp_animals %>%
  knitr::kable("html",
               digits = 4,
               col.names = c("Model",
                             rep(c("Estimate", "Lower CI", "Upper CI"), 3))) %>%
  add_header_above(c(" " = 1,
                     "Fungicide" = 3,
                     "Herbicide" = 3,
                     "Insecticide" = 3)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))



save_kable(table_animals, "output/animals_comparison.pdf")
```


### Correlation coefficients for VCV matrix (0.1-0.9)

Now we look at the effect of the two correlation coefficients used in the covariance matrix. This is long so commented 

```{r}
# rho_range <- seq(0.5, 0.95, by = 0.05)
# phi_range <- seq(0.5, 0.95, by = 0.05)
# 
# rho_est <- final_est_imputed
# 
# for (i in 1:length(rho_range)){
#   for (j in 1:length(phi_range)){
#   rho_matrix <- metafor::vcalc(vi = LRR_VAR_INDIVIDUAL,
#                cluster = STUDY_ID,
#                obs = MULTIPLE_TYPE,
#                grp1 = CONTROL_GROUP,
#                grp2 = TEST_GROUP,
#                w1 = AI_N_INDIVIDUAL,
#                w2 = FORM_N_INDIVIDUAL,
#                time1 = TIME_SIMPLE,
#                rho = rho_range[i],
#                phi= phi_range[j],
#                data= data_cleaned_imputed)
# 
#   rho_model <- rma.mv(yi = LRR, V = rho_matrix,
#                                 mod = ~ 0 + PESTICIDE_CLASS,
#                                 random = list(~1 | STUDY_ID,
#                                               ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
#                                 struct = "AR",
#                                 data = data_cleaned_imputed, method = "REML", test = "t", dfs = "contain")
#   
#   est <- estim_mod_wide(rho_model, paste0("rho = ", rho_range[i], "phi =", phi_range [j]))
#   
#   rho_est <- bind_rows(rho_est, est)
#   
#   }
# }
# 
# table_rho <- rho_est %>%
#   knitr::kable("html",
#                digits = 4,
#                col.names = c("Model",
#                              rep(c("Estimate", "Lower CI", "Upper CI"), 3))) %>%
#   add_header_above(c(" " = 1,
#                      "Fungicide" = 3,
#                      "Herbicide" = 3,
#                      "Insecticide" = 3)) %>%
#   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
# 
# 
# 
# save_kable(table_rho, "output/sensitivity_correlation_coefficients.pdf")
# 
# write_csv(rho_est, "output/sensitivity_correlation_coefficient.csv")

```

```{r}
rho_est <-  read_csv("output/sensitivity_correlation_coefficient.csv")

# Long format 

rho_long <- rho_est %>%
  pivot_longer(
    cols = -model,
    names_to = c(".value", "pesticide_class"),
    names_pattern = "(estimate|lower|upper)_(.*)") %>%
  extract(model, into = c("rho", "phi"), regex = "rho *= *([0-9.]+).*phi *= *([0-9.]+)", remove = FALSE) %>%
  mutate(
    rho = as.numeric(rho),
    phi = as.numeric(phi)
  ) %>%
  filter(!is.na(rho))

ggplot(rho_long,
       aes(x = rho, y = estimate, ymin = lower, ymax = upper, color = pesticide_class)) +
  geom_line() +
  geom_ribbon(aes(fill = pesticide_class), alpha = 0.2, color = NA) +
  facet_wrap(~ pesticide_class) +
  theme_bw() +
  labs( x = "Rho", y = "Effect Estimate") +
  theme(legend.position = "none")

ggplot(rho_long,
       aes(x = phi, y = estimate, ymin = lower, ymax = upper, color = pesticide_class)) +
  geom_line() +
  geom_ribbon(aes(fill = pesticide_class), alpha = 0.2, color = NA) +
  facet_wrap(~ pesticide_class) +
  theme_bw() +
  labs(x = "Phi", y = "Effect Estimate") +
  theme(legend.position = "none")


```


### Excluded

I don't think this has too much importance because there are only 4 rows that can be reintegrated in the analysis, and they haven't been through the imputation stage. There are results for this in the previous version. 


### Sample size

Here we look at the influence of the decision to use the individual sample size in all the formulas. We test:  
1) Container level sample size 
2) Effective Sample size where a 0.046 ICC (Intraclass Correlation Coefficient) was used, which was calculated from a paper within the meta-analysis
3) Effective Sample size where a 0.4ish ICC, as this was the maximum ICC from the papers within the meta-analysis where an ICC could be calculated.



```{r, warning=FALSE}
# Creating a new dataset and using container sample size
# However it can't be sample size can't be 1 so have to change it first 

sample_size_sensitivity_df <- data_cleaned_not_imputed %>%
  mutate(
    # Force n = 2 if n = 1
    AI_N_CONTAINER = if_else(AI_N_CONTAINER == 1, 2L, AI_N_CONTAINER),  
    FORM_N_CONTAINER = if_else(FORM_N_CONTAINER == 1, 2L, FORM_N_CONTAINER),
    # Computing SE for CI and SD
    AI_SE_CONTAINER = case_when(
      AI_ERROR_TYPE == "CI_95" ~ AI_BIGGEST_CI_ARM / -qt(.025, df = AI_N_CONTAINER -1),
      AI_ERROR_TYPE == "SD" ~ AI_ERROR_LOWER/sqrt(AI_N_CONTAINER),
      AI_ERROR_TYPE == "SE" ~ AI_SE_INDIVIDUAL
    ),
    FORM_SE_CONTAINER = case_when(
      FORM_ERROR_TYPE == "CI_95" ~ FORM_BIGGEST_CI_ARM / -qt(.025, df = FORM_N_CONTAINER -1),
      FORM_ERROR_TYPE == "SD" ~ FORM_ERROR_LOWER/sqrt(FORM_N_CONTAINER),
      FORM_ERROR_TYPE == "SE" ~ FORM_SE_INDIVIDUAL
    ),
    # Average cluster size
    AVERAGE_CLUSTER_SIZE = ((AI_N_CONTAINER*AI_N_INDIVIDUALS_PER_CONTAINER)+ (FORM_N_CONTAINER*FORM_N_INDIVIDUALS_PER_CONTAINER)) / (AI_N_CONTAINER + FORM_N_CONTAINER),
    # Design effect for 0.442 ICC
    DESIGN_EFFECT_0.442_ICC = 1 + (AVERAGE_CLUSTER_SIZE - 1) * 0.442, 
     # ESS for ai based on 0.442 ICC
    AI_ESS_0.442_ICC = AI_N_INDIVIDUAL / DESIGN_EFFECT_0.442_ICC,
    # ESS for form based on 0.442 ICC
    FORM_ESS_0.442_ICC = FORM_N_INDIVIDUAL / DESIGN_EFFECT_0.442_ICC,
    # design effect for 0.046 ICC
    DESIGN_EFFECT_0.046_ICC = 1 + (AVERAGE_CLUSTER_SIZE - 1) * 0.046,
    # ESS for ai based on 0.046 ICC
    AI_ESS_0.046_ICC = AI_N_INDIVIDUAL / DESIGN_EFFECT_0.046_ICC,
    # ESS for FORM based on 0.046 ICC
    FORM_ESS_0.046_ICC = FORM_N_INDIVIDUAL / DESIGN_EFFECT_0.046_ICC,
    # FORM SE calculation using ESS (ICC = 0.442)
    FORM_SE_ESS_0.442 = case_when(
      FORM_ERROR_TYPE == "CI_95" ~ FORM_BIGGEST_CI_ARM / -qt(.025, df = FORM_ESS_0.442_ICC -1),
      FORM_ERROR_TYPE == "SD" ~ FORM_ERROR_LOWER/sqrt(FORM_ESS_0.442_ICC),
      FORM_ERROR_TYPE == "SE" ~ FORM_SE_INDIVIDUAL
    ),
    # FORM SE calculation using ESS (ICC = 0.046)
    FORM_SE_ESS_0.446 = case_when(
      FORM_ERROR_TYPE == "CI_95" ~ FORM_BIGGEST_CI_ARM / -qt(.025, df = FORM_ESS_0.046_ICC -1),
      FORM_ERROR_TYPE == "SD" ~ FORM_ERROR_LOWER/sqrt(FORM_ESS_0.046_ICC),
      FORM_ERROR_TYPE == "SE" ~ FORM_SE_INDIVIDUAL
    ),
    # AI SE calculation using ESS (ICC = 0.442)
    AI_SE_ESS_0.442 = case_when(
      AI_ERROR_TYPE == "CI_95" ~ AI_BIGGEST_CI_ARM / -qt(.025, df = AI_ESS_0.442_ICC -1),
      AI_ERROR_TYPE == "SD" ~ AI_ERROR_LOWER/sqrt(AI_ESS_0.442_ICC),
      AI_ERROR_TYPE == "SE" ~ AI_SE_INDIVIDUAL
    ), 
    # AI SE calculation using ESS (ICC = 0.046)
    AI_SE_ESS_0.446 = case_when(
      AI_ERROR_TYPE == "CI_95" ~ AI_BIGGEST_CI_ARM / -qt(.025, df = AI_ESS_0.046_ICC -1),
      AI_ERROR_TYPE == "SD" ~ AI_ERROR_LOWER/sqrt(AI_ESS_0.046_ICC),
      AI_ERROR_TYPE == "SE" ~ AI_SE_INDIVIDUAL),
    # SD CALCULATIONS 
    AI_SD_CONTAINER = AI_SE_CONTAINER * sqrt(AI_N_CONTAINER),
    AI_SD_ESS_0.446 = AI_SE_ESS_0.446 * sqrt(AI_ESS_0.046_ICC),
    AI_SD_ESS_0.442 = AI_SE_ESS_0.442 * sqrt(AI_ESS_0.442_ICC),
    FORM_SD_CONTAINER = FORM_SE_CONTAINER * sqrt(FORM_N_CONTAINER),
    FORM_SD_ESS_0.446 = FORM_SE_ESS_0.446 * sqrt(FORM_ESS_0.046_ICC),
    FORM_SD_ESS_0.442 = FORM_SE_ESS_0.442 * sqrt(FORM_ESS_0.442_ICC),
    # CV Calculation (will be NA if needs to be imputed)
    CV_AI_CONTAINER = na_if(AI_SD_CONTAINER/AI_50, Inf),
    CV_AI_ESS_0.046 = na_if(AI_SD_ESS_0.446/AI_50, Inf),
    CV_AI_ESS_0.442 = na_if(AI_SD_ESS_0.442/AI_50, Inf),
    CV_FORM_CONTAINER = na_if(FORM_SD_CONTAINER/AI_50, Inf),
    CV_FORM_ESS_0.046 = na_if(FORM_SD_ESS_0.446/AI_50, Inf),
    CV_FORM_ESS_0.442 = na_if(FORM_SD_ESS_0.442/AI_50, Inf)) 


    
# Doing the imputations with the different sample sizes 
# Computing the CV2 for missing case

sample_size_sensitivity_df <- cv_avg(x = AI_50, sd = AI_SD_CONTAINER,
                            n = AI_N_CONTAINER, group = STUDY_ID, label = "CONTAINER_AI",
                             data = sample_size_sensitivity_df)

sample_size_sensitivity_df <- cv_avg(x = FORM_50, sd = FORM_SD_CONTAINER,
                            n = FORM_N_CONTAINER, group = STUDY_ID,
                            label = "CONTAINER_FORM", data = sample_size_sensitivity_df)

sample_size_sensitivity_df <- cv_avg(x = AI_50, sd = AI_SD_ESS_0.446,
                            n = AI_ESS_0.046_ICC, group = STUDY_ID, label = "ESS_0.046_AI",
                             data = sample_size_sensitivity_df)

sample_size_sensitivity_df <- cv_avg(x = FORM_50, sd = FORM_SD_ESS_0.446,
                            n = FORM_ESS_0.046_ICC, group = STUDY_ID,
                            label = "ESS_0.046_FORM", data = sample_size_sensitivity_df)

sample_size_sensitivity_df <- cv_avg(x = AI_50, sd = AI_SD_ESS_0.442,
                            n = AI_ESS_0.442_ICC, group = STUDY_ID, label = "ESS_0.442_AI",
                             data = sample_size_sensitivity_df)

sample_size_sensitivity_df <- cv_avg(x = FORM_50, sd = FORM_SD_ESS_0.442,
                            n = FORM_ESS_0.442_ICC, group = STUDY_ID,
                            label = "ESS_0.442_FORM", data = sample_size_sensitivity_df)

# Building the CV2 accrding to missing case or not

sample_size_sensitivity_df <- sample_size_sensitivity_df %>%
   mutate(CV2_CONTAINER_AI= if_else(is.na(CV_AI_CONTAINER),b_CV2_CONTAINER_AI, CV_AI_CONTAINER^2),
          CV2_CONTAINER_FORM = if_else(is.na(CV_FORM_CONTAINER), b_CV2_CONTAINER_FORM, CV_FORM_CONTAINER^2),
          CV2_ESS_0.046_AI= if_else(is.na(CV_AI_ESS_0.046),b_CV2_ESS_0.046_AI, CV_AI_ESS_0.046^2),
          CV2_ESS_0.046_FORM= if_else(is.na(CV_FORM_ESS_0.046),b_CV2_ESS_0.046_FORM, CV_FORM_ESS_0.046^2),
          CV2_ESS_0.442_AI= if_else(is.na(CV_AI_ESS_0.442),b_CV2_ESS_0.442_AI, CV_AI_ESS_0.442^2),
          CV2_ESS_0.442_FORM= if_else(is.na(CV_FORM_ESS_0.442),b_CV2_ESS_0.442_FORM, CV_FORM_ESS_0.046^2))


# Compute variance

sample_size_sensitivity_df <- sample_size_sensitivity_df %>%
  mutate(LRR_VAR_CONTAINER = v_lnrr_laj(cv1 = CV2_CONTAINER_AI,
                                        n1= AI_N_CONTAINER,
                                        cv2 = CV2_CONTAINER_FORM,
                                        n2 = FORM_N_CONTAINER),
         LRR_VAR_ESS_0.046 =  v_lnrr_laj(cv1 = CV2_ESS_0.046_AI,
                                         n1= AI_ESS_0.046_ICC,
                                         cv2 = CV2_ESS_0.046_FORM,
                                         n2 = FORM_ESS_0.046_ICC),
         LRR_VAR_ESS_0.442 =  v_lnrr_laj(cv1 = CV2_ESS_0.442_AI,
                                         n1= AI_ESS_0.442_ICC,
                                         cv2 = CV2_ESS_0.442_FORM,
                                         n2 = FORM_ESS_0.442_ICC))



# specify the final model 4 times with the different variances and compare results
# Cannot use fitmod because the columns are different 


# final model with icc_0.046_level_vi
icc_0.046_sample_autocorrelation_matrix <- metafor::vcalc(vi =LRR_VAR_ESS_0.046,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_ESS_0.046_ICC,
               w2 = FORM_ESS_0.046_ICC,
               time1 = TIME_SIMPLE,
               rho = 0.8,
               phi= 0.8,
               data= sample_size_sensitivity_df)

icc_0.046_sample_final_model <- rma.mv(yi = LRR, V = icc_0.046_sample_autocorrelation_matrix,
                    mod = ~ 0 + PESTICIDE_CLASS,
                    random = list(~1 | STUDY_ID,
                                  ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                    struct = "AR",
                    data = sample_size_sensitivity_df, method = "REML", test = "t", dfs = "contain")

# final model with icc_0.442_level_vi
icc_0.442_sample_autocorrelation_matrix <- metafor::vcalc(vi =LRR_VAR_ESS_0.442,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_ESS_0.442_ICC,
               w2 = FORM_ESS_0.442_ICC,
               time1 = TIME_SIMPLE,
               rho = 0.8,
               phi= 0.8,
               data= sample_size_sensitivity_df)

icc_0.442_sample_final_model <- rma.mv(yi = LRR, V = icc_0.442_sample_autocorrelation_matrix,
                    mod = ~ 0 + PESTICIDE_CLASS,
                    random = list(~1 | STUDY_ID,                                 
                                  ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                    struct = "AR",
                    data = sample_size_sensitivity_df, method = "REML", test = "t", dfs = "contain")

# final model with container_level_vi
container_sample_autocorrelation_matrix <- metafor::vcalc(vi = LRR_VAR_CONTAINER,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_N_CONTAINER,
               w2 = FORM_N_CONTAINER,
               time1 = TIME_SIMPLE,
               rho = 0.8,
               phi= 0.8,
               data= sample_size_sensitivity_df)

container_sample_final_model <- rma.mv(yi = LRR, V = container_sample_autocorrelation_matrix,
                    mod = ~ 0 + PESTICIDE_CLASS,
                    random = list(~1 | STUDY_ID,                                 
                                  ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                    struct = "AR",
                    data = sample_size_sensitivity_df, method = "REML", test = "t", dfs = "contain")


# table
lrr_variances_comparison_table_df <- bind_rows(final_est_imputed %>% mutate(model = "individual"),
                                               estim_mod_wide(icc_0.046_sample_final_model,"effective, ICC = 0.046" ),
                                               estim_mod_wide(icc_0.442_sample_final_model, "effective, ICC = 0.442"),
                                               estim_mod_wide(container_sample_final_model, "container"))

table_samplesize <- lrr_variances_comparison_table_df %>%
  knitr::kable("html",
               digits = 4,
               col.names = c("Model",
                             rep(c("Estimate", "Lower CI", "Upper CI"), 3))) %>%
  add_header_above(c(" " = 1,
                     "Fungicide" = 3,
                     "Herbicide" = 3,
                     "Insecticide" = 3)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))



save_kable(table_samplesize, "output/samplesize_comparison.pdf")

# Plotting 

container_plot <- orchard_plot(container_sample_final_model, 
                                         mod = "PESTICIDE_CLASS", 
                                         xlab = "Effect size lnRR", 
                                         group = "STUDY_ID",  k = TRUE, g = TRUE, trunk.size = 1.5) +
  scale_fill_manual(values = c("#CC79A7", "#009E73", "#F0E442")) +
  scale_colour_manual(values = c("#CC79A7", "#009E73", "#F0E442"))+
  ggtitle("Container sample size")

icc442_plot <- orchard_plot(icc_0.442_sample_final_model, 
                                         mod = "PESTICIDE_CLASS", 
                                         xlab = "Effect size lnRR", 
                                         group = "STUDY_ID",  k = TRUE, g = TRUE, trunk.size = 1.5) +
  scale_fill_manual(values = c("#CC79A7", "#009E73", "#F0E442")) +
  scale_colour_manual(values = c("#CC79A7", "#009E73", "#F0E442"))+
  ggtitle("ESS ICC = 0.442")

icc46_plot <- orchard_plot(icc_0.046_sample_final_model, 
                                         mod = "PESTICIDE_CLASS", 
                                         xlab = "Effect size lnRR", 
                                         group = "STUDY_ID",  k = TRUE, g = TRUE, trunk.size = 1.5) +
  scale_fill_manual(values = c("#CC79A7", "#009E73", "#F0E442")) +
  scale_colour_manual(values = c("#CC79A7", "#009E73", "#F0E442"))+
  ggtitle("ESS ICC = 0.046")

individual <- final_imputed_plot + ggtitle("Individual sample size")


cairo_pdf("output/Sample_size_influence_plots.pdf", width = 10, height = 12)

(individual + container_plot) / (icc442_plot + icc46_plot)  

dev.off()

```




## Other analysis

### Effect of glyphosate


```{r}
# Defining a function to fit a model with no moderators 
fit_mod_one <- function(data){
  matrix_one <- metafor::vcalc(vi = LRR_VAR_INDIVIDUAL,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_N_INDIVIDUAL,
               w2 = FORM_N_INDIVIDUAL,
               time1 = TIME_SIMPLE,
               phi = 0.8,
               rho = 0.8,
               data= data)

  model_one <- rma.mv(yi = LRR, V = matrix_one,
                                mod = ~ 1,
                                random = list(~1 | STUDY_ID,
                                              ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                                struct = "AR",
                                data = data, method = "REML", test = "t", dfs = "contain")

  
  return(model_one)
  }
```


```{r}
data_not_imputed_glyphosate <- data_cleaned_no_missing %>%
  filter(AI_NAME %in% c("glyphosate", "glyphosate-ipa", "glyphosate ipa salt"))

data_imputed_gly <- data_cleaned_imputed %>%
    filter(AI_NAME %in% c("glyphosate", "glyphosate-ipa", "glyphosate ipa salt"))

data_other_imputed <- data_cleaned_no_missing%>%
  filter(PESTICIDE_CLASS == "herbicide") %>%
    filter(!AI_NAME %in% c("glyphosate", "glyphosate-ipa", "glyphosate ipa salt"))


mod_no_gly <- fit_mod_one(data_other_imputed)

mod_gly_no_imp <- fit_mod_one(data_not_imputed_glyphosate)

mod_gly_imp <- fit_mod_one(data_imputed_gly)

est_gly_imp <- estim_mod_wide(mod_gly_imp, "Glyphosate imputed")
est_no_gly <- estim_mod_wide(mod_no_gly, "Herbicides without glyphosate")
est_gly_no_imp <- estim_mod_wide(mod_gly_no_imp, "Glyphosate not imputed")

comp_gly_other <- bind_rows(est_gly_imp, est_no_gly)
comp_gly_imp <- bind_rows(est_gly_imp, est_gly_no_imp)

# Saving 

table_gly <- comp_gly_other %>%
  knitr::kable("html",
               digits = 4,
               col.names = c("Model",
                             rep(c("Estimate", "Lower CI", "Upper CI"), 1))) %>%
  add_header_above(c(" " = 1,
                     "Herbicide" = 3)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))



save_kable(table_gly, "output/glyphosate_herbicide_comparison.pdf")



table_gly_imp <- comp_gly_imp %>%
  knitr::kable("html",
               digits = 4,
               col.names = c("Model",
                             rep(c("Estimate", "Lower CI", "Upper CI"), 1))) %>%
  add_header_above(c(" " = 1,
                     "Herbicide" = 3)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))



save_kable(table_gly_imp, "output/glyphosate_imputation_comparison.pdf")


# Plots 

gly_imp_plot <- orchard_plot(mod_gly_imp,
                                        xlab = "Effect size lnRR",
                                        group = "STUDY_ID",  k = TRUE, g = TRUE, trunk.size = 1.5) +
  scale_fill_manual(values = c("#90EE90")) +
  scale_colour_manual(values = c("#90EE90")) +
  ggtitle("Glyphosate with imputation")

gly_plot <- orchard_plot(mod_gly_no_imp,
                                        xlab = "Effect size lnRR",
                                        group = "STUDY_ID",  k = TRUE, g = TRUE, trunk.size = 1.5) +
  scale_fill_manual(values = c("#90EE90")) +
  scale_colour_manual(values = c("#90EE90")) +
  ggtitle("Glyphosate without imputation")

herb_plot <- orchard_plot(mod_no_gly,
                                        xlab = "Effect size lnRR",
                                        group = "STUDY_ID",  k = TRUE, g = TRUE, trunk.size = 1.5) +
  scale_fill_manual(values = c("#90EE90")) +
  scale_colour_manual(values = c("#90EE90")) +
  ggtitle("Other herbicides with imputation")


cairo_pdf("output/glyphosate_comparison_orchard_plot.pdf")
gly_imp_plot / gly_plot
dev.off()

cairo_pdf("output/glyphosate_herb_comparison_orchard_plot.pdf")
herb_plot / gly_imp_plot
dev.off()

```

Let's look at the diversity of formulations in glyphosate 

```{r}
gly_form_n <- length(unique(data_imputed_gly$FORM_NAME))
gly_form_n

herb_form_n <- length(unique(data_other_imputed$FORM_NAME))
herb_form_n
```
There are almost the same number of formulations in all other herbicides than in glyphosate. 


### Roundup and glyophosate 

*Look for the decline effect in glyphosate/roundup studies. Not present in either the non-imputed or imputed datasets. This is a pretty crude analysis. I've based Roundup composition changing according to year, which may not be strictly be true. Some of the countries these tests were performed in may have less stringent regulatory bodies, where it takes longer to restrict more toxic co-formulants.*


```{r}

# imputed
roundup_only_imputed  <- data_cleaned_imputed %>%
  filter(str_detect(FORM_NAME, "Roundup")) %>%
  mutate(YEAR_CEN = YEAR_PUBLISHED - mean(YEAR_PUBLISHED, na.rm = TRUE))

# not imputed
roundup_only <- data_cleaned_no_missing %>%
  filter(str_detect(FORM_NAME, "Roundup")) %>%
  mutate(YEAR_CEN = YEAR_PUBLISHED - mean(YEAR_PUBLISHED, na.rm = TRUE))

# Fitting models 
# Not imputed
  
autocorrelation_matrix_roundup <- metafor::vcalc(vi = LRR_VAR_INDIVIDUAL,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_N_INDIVIDUAL,
               w2 = FORM_N_INDIVIDUAL,
               time1 = TIME_SIMPLE,
               phi = 0.8,
               rho = 0.8,
               data= roundup_only)
  
roundup_model <- rma.mv(yi = LRR, V = autocorrelation_matrix_roundup,
                                          mod = ~ YEAR_CEN,
                                          random = list(~1 | STUDY_ID,
                                                        ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                                          struct = "AR",
                                          data = roundup_only, method = "REML", test = "t", dfs = "contain")
  

# Making predictions for the plot 
roundup_year_cen_pred <- predict(roundup_model,
                                 newmods = seq(min(roundup_only$YEAR_CEN),
                                               max(roundup_only$YEAR_CEN),
                                               length.out = nrow(roundup_only)))

predictions_roundup <- data.frame(YEAR_PUBLISHED = seq(min(roundup_only$YEAR_PUBLISHED),
                                                       max(roundup_only$YEAR_PUBLISHED),
                                                       length.out=nrow(roundup_only)),
                                  fit = roundup_year_cen_pred$pred,
                                  upper = roundup_year_cen_pred$ci.ub,
                                  lower = roundup_year_cen_pred$ci.lb)
# Plotting
roundup_plot <- ggplot() +
  geom_point(data = roundup_only, aes(x = YEAR_PUBLISHED, y = LRR)) +
  geom_line(data = predictions_roundup, aes(x = YEAR_PUBLISHED, y = fit)) +
  geom_ribbon(data = predictions_roundup, aes(x = YEAR_PUBLISHED, y = fit, ymin = lower, ymax = upper, alpha = 0.3)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  xlab("Year of Publication") +
  ylab("Effect size (lnRR)") +
  ggtitle("Does the effect size magnitude for Roundup formulations reduce with time?") +
  theme(legend.position = "none")

# Imputed


autocorrelation_matrix_roundup_imp <- metafor::vcalc(vi = LRR_VAR_INDIVIDUAL,
               cluster = STUDY_ID,
               obs = MULTIPLE_TYPE,
               grp1 = CONTROL_GROUP,
               grp2 = TEST_GROUP,
               w1 = AI_N_INDIVIDUAL,
               w2 = FORM_N_INDIVIDUAL,
               time1 = TIME_SIMPLE,
               phi = 0.8,
               rho = 0.8,
               data= roundup_only_imputed)
  
roundup_model_imp <- rma.mv(yi = LRR, V = autocorrelation_matrix_roundup_imp,
                                          mod = ~ YEAR_CEN,
                                          random = list(~1 | STUDY_ID,
                                                        ~ TIME_SIMPLE | MULTIPLE_MEASUREMENT),
                                          struct = "AR",
                                          data = roundup_only_imputed, method = "REML", test = "t", dfs = "contain")

summary(roundup_model_imp)

robust(roundup_model_imp, cluster = roundup_only_imputed$STUDY_ID, clubSandwich = TRUE)



roundup_year_cen_pred_imp <- predict(roundup_model_imp,
                                 newmods = seq(min(roundup_only_imputed$YEAR_CEN),
                                               max(roundup_only_imputed$YEAR_CEN),
                                               length.out = nrow(roundup_only_imputed)))

predictions_roundup_imp <- data.frame(YEAR_PUBLISHED = seq(min(roundup_only_imputed$YEAR_PUBLISHED),
                                                       max(roundup_only_imputed$YEAR_PUBLISHED),
                                                       length.out=nrow(roundup_only_imputed)),
                                  fit = roundup_year_cen_pred_imp$pred,
                                  upper = roundup_year_cen_pred_imp$ci.ub,
                                  lower = roundup_year_cen_pred_imp$ci.lb)

roundup_plot_imp <- ggplot() +
  geom_point(data = roundup_only_imputed, aes(x = YEAR_PUBLISHED, y = LRR), alpha = 0.5, colour = 'darkgreen') +
  geom_line(data = predictions_roundup_imp, aes(x = YEAR_PUBLISHED, y = fit), colour = 'darkgreen') +
  geom_ribbon(data = predictions_roundup_imp, aes(x = YEAR_PUBLISHED, y = fit, ymin = lower, ymax = upper, alpha = 0.3 )) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  xlab("Year of Publication") +
  ylab("Effect size (lnRR)") +
  #ggtitle("Does the effect size magnitude for Roundup formulations reduce with time? (Imputed data)") +
  theme(legend.position = "none")
  
cairo_pdf("output/roundup_decline_effect_plot.pdf")
roundup_plot_imp
dev.off()
```

Even if it looks like there is a trend in the plot, it is not significant in the model. 


### Plot of relative PPP mortality.

Fit an intercept only model. Generate an Orchard plot, then put horizontal dashed lines denoting the half and double toxic thresholds. Use the imputed data as I am only looking at the LRR for this, which isn't impacted by SE.

```{r}

color_above <- log(2)
color_below <- log(0.5)


data_cleaned_imputed <- data_cleaned_imputed %>%
  mutate(color = if_else(LRR > log(2) | LRR < log(0.5), "color", NA_character_))

nabove <- data_cleaned_imputed %>% filter(LRR > log(2)) %>% nrow()
nbelow <-  data_cleaned_imputed %>% filter(LRR < log(0.5)) %>% nrow()

factor_two_mortality_diff_plot <- ggplot(data_cleaned_imputed, aes(x = "", y = LRR, size = 1/sqrt(LRR_VAR_INDIVIDUAL), alpha = 0.5, color = color)) +
  geom_quasirandom() +
  coord_flip() +
  theme_bw() +
  theme(legend.position = "none") +
  ylab("Effect Size (lnRR)") +
  xlab("") +
  geom_hline(yintercept = 0, linetype = 2, colour = "black", alpha = 0.5) +
  geom_hline(yintercept = log(0.5), linetype = 2, colour = "#8B0000", alpha = 0.5) +
  geom_hline(yintercept = log(2), linetype = 2, colour = "#8B0000", alpha = 0.5) +
  ggtitle("PPP, AI pairs where mortality differs by > factor 2") +
  scale_color_manual(values = "#8B0000") +
  annotate("text", x = 1.5, y = -4, label = paste0("Effect sizes < ln(0.5) = ",
                                                   nbelow, sep = "")) +
  annotate("text", x = 1.5, y = 0, label = paste0("Effect sizes > ln(2) = ",
                                                 nabove, sep = ""))

factor_two_mortality_diff_plot

facet_labels <- c(
  "fungicide" = "Fungicide",
  "herbicide" = "Herbicide",
  "insecticide" = "Insecticide"
)

factor_two_mortality_diff_plot_facet <- ggplot(data_cleaned_imputed,
    aes(x = "",  
        y = LRR,
        size = 1 / sqrt(LRR_VAR_INDIVIDUAL),
        alpha = 0.5,
        color = color)) +
  coord_flip()+
  geom_quasirandom() +
  facet_grid(PESTICIDE_CLASS ~ ., labeller = labeller(PESTICIDE_CLASS = facet_labels)) +  
  theme_bw() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.background = element_line(fill = "grey90"),  # Removes the grey box
  strip.text = element_text(size = 12, face = "bold"),
        strip.text = element_text(size = 12)) +
  ylab("Effect Size (lnRR)") +
  xlab("") +
  geom_hline(yintercept = 0, linetype = 2, colour = "black", alpha = 0.5) +
  geom_hline(yintercept = log(0.5), linetype = 2, colour = "#8B0000", alpha = 0.5) +
  geom_hline(yintercept = log(2), linetype = 2, colour = "#8B0000", alpha = 0.5) +
  #ggtitle("PPP, AI pairs where mortality differs by > factor 2") +
  scale_color_manual(values = "#8B0000")

factor_two_mortality_diff_plot_facet

# use cowplot to create a grid
cairo_pdf("output/factor_two_mortality_diff_plot.pdf", width = 10, height = 6)
factor_two_mortality_diff_plot
dev.off()

cairo_pdf("output/mortality_two_facet_plot.pdf", width = 10, height = 6)
factor_two_mortality_diff_plot_facet
dev.off()
```